---
title: "Accumulation Curve Fitting"
output: html_notebook
---

The next step in this analysis is to examine how these effects differ as a function
of the number of samples included -- are effects strongest locally and linearly
decline? Or do they show a nonlinear pattern? How important are spatial distributions?  

Here, I generate accumulation curves for each plot to capture these effects. The 
first approach, the "empirical" accumulation curve captures the effects of both
plot community composition and spatial distribution. The second, the "random" accumulation
curve, randomizes plot positions to remove these spatial effects, and can serve 
as a null model.

## Loading in datasets

```{r}
load("../Data/biodiv_dat.RData")
```

## Loading Functions

```{r}
library(tidyverse); library(gridExtra); library(lme4)
source("diversity_metrics.R")
source("gamma_permutation.R")
source("rarefaction_permutation.R")
```

---

## Accumulation at q = 0

### Generating empirical accumulation curves
```{r}
if(!file_test("-f", "../Data/curve_sims_q0.rds")){
  output <- list()
  
  for(i in 1:length(splitmat)){
    spatperm <- permute_spatial(as.data.frame(splitmat[[i]]),
                                coords = splitatt[[i]] %>% dplyr::select(subplotx, subploty),
                                treatment = rep(1, nrow(splitmat[[i]])),
                                nperm = 999)
    id <- list(id = unique(splitatt[[i]][,c(1:3, 7)]))
    
    output <- append(output, 
                     list(append(spatperm, id)))
    
    print(paste("Finished run", i, "of", length(splitmat)))
  }
  
 saveRDS(output, file = "../Data/curve_sims_q0.rds")
}
```

```{r, warning=FALSE}
perm_func <- function(x, plotxy){
  mobr::rarefaction(x[shuffle(x),], coords = plotxy, method = "spat", latlong = FALSE)
}


if(!file_test("-f", "../Data/curve_sims_q0_v2.rds")){
  output <- list()
  
  for(i in 1:length(splitmat)){
    
    spatperm <- mobr::rarefaction(splitmat[[i]], coords = splitatt[[i]][,c('subplotx', 'subploty')], method = "spat", latlong = FALSE)

    permoutput <- t(replicate(n = 999, perm_func(splitmat[[i]], splitatt[[i]][,c('subplotx', 'subploty')])))

    spatrand <- cbind(perm = c(1:nrow(permoutput)),
                           permoutput)
    
    id <- list(id = unique(splitatt[[i]][,c(1:3, 7)]))
    
    output <- append(output, 
                     list(append(
                       list(data.frame(t(spatperm)), data.frame(spatrand)),
                       id)
                       )
                     )
    if(i %% 12 == 0){
    print(paste("Finished run", i, "of", length(splitmat)))
    }
  }
  
 saveRDS(output, file = "../Data/curve_sims_q0_v2.rds")
}

```


## Gathering data

```{r}
# Species richness
curves_q0 <- readRDS("../Data/curve_sims_q0_v2.rds")
spat_curves_q0 <- lapply(curves_q0, '[[', 1) %>% lapply(., function(x) data.frame(x))
curveids_q0 <- lapply(curves_q0, '[[', 3)
rand_curves_q0 <- lapply(curves_q0, '[[', 2)

add_labels <- function(x, y){
  curves_with_ids <- list()
  for(i in 1:length(x)){
    curves_with_ids[[i]] <- cbind(x[[i]], y[[i]])
  }
  return(curves_with_ids)
}

# Species richness
q0_spat <- add_labels(curveids_q0, spat_curves_q0) %>% bind_rows(.)
q0_rand <- add_labels(curveids_q0, rand_curves_q0) %>% bind_rows(.)

```

## Plotting empirical curves

```{r}
sitelabels <- read.csv(file = "../Data/FinalDatasets/Site_Descriptions.csv")

q0_spat <- inner_join(sitelabels, q0_spat, by = c("plot" = "plotno", "site" = "site", "block" = "blockno"))

SAR_block <- q0_spat %>%
  select(-sitename, -dateestablished) %>%
  pivot_longer(-c("site", "year", "fertilized", "block", "plot"),
               names_to = "samp_effort",
               values_to = "diversity") %>%
  mutate(samp_effort = gsub("X", "", samp_effort)) %>%
  filter(samp_effort %in% c(1,2,4,8,16,32,64))

SAR_mean <- q0_spat %>% group_by(year, fertilized) %>% summarise_if(is.numeric, mean) %>%
  pivot_longer(-c("year", "fertilized", "block", "plot"),
               names_to = "samp_effort",
               values_to = "diversity") %>%
  mutate(samp_effort = gsub("X", "", samp_effort)) %>%
  filter(samp_effort %in% c(1,2,4,8,16,32,64))

rawplot <- SAR_block %>%
  ggplot(aes(x = as.numeric(samp_effort),
             y = diversity,
             color = as.factor(fertilized),
             fill = as.factor(fertilized),
             group = paste(site, block, fertilized))) +
  geom_line(data = SAR_mean, aes(group = NULL), size = 2) + 
  geom_line(alpha = .4, size = .5) + 
  # geom_point(shape = 21, alpha = .4) +
  geom_point(shape = 21, data = SAR_mean, aes(group = NULL), color = 'black', size = 2) +
  facet_wrap(~year) +
  theme_bw() +
  scale_fill_manual(name = 'Treatment',
                    labels = c('Control', '+N'),
                    values = c("#357EBDFF", "#D43F3AFF")) +
  scale_color_manual(name = 'Treatment',
                    labels = c('Control', '+N'),
                    values = c("#357EBDFF", "#D43F3AFF")) +
  ylab("Species Richness") +
  xlab("Number of Samples") +
  ggtitle("a) SAC - Untransformed")
  

logplot <- SAR_block %>%
  ggplot(aes(x = log(as.numeric(samp_effort)),
             y = log(diversity),
             color = as.factor(fertilized),
             fill = as.factor(fertilized),
             group = paste(site, block, fertilized))) +
  geom_line(data = SAR_mean, aes(group = NULL), size = 2) + 
  geom_line(alpha = .4, size = .5) + 
  # geom_point(shape = 21, alpha = .4) +
  geom_point(shape = 21, data = SAR_mean, aes(group = NULL), color = 'black', size = 2) +
  facet_wrap(~year) +
  theme_bw() +
  scale_fill_manual(name = 'Treatment',
                    labels = c('Control', '+N'),
                    values = c("#357EBDFF", "#D43F3AFF")) +
  scale_color_manual(name = 'Treatment',
                    labels = c('Control', '+N'),
                    values = c("#357EBDFF", "#D43F3AFF")) +
  ylab("log(Species Richness)") +
  xlab("log(Number of Samples)") +
  ggtitle("b) SAC - Log Scale")

g_legend<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)}

mylegend<-g_legend(rawplot)

p3 <- arrangeGrob(arrangeGrob(rawplot + theme(legend.position="none"),
                         logplot + theme(legend.position="none"),
                         nrow=2),
             mylegend, nrow=1,widths =c(6, 1))


summary(lmer(log(diversity) ~ log(as.numeric(samp_effort)) * fertilized + (1 | site:block),
     data = SAR_block %>% filter(year == 2017)))
summary(lmer(log(diversity) ~ log(as.numeric(samp_effort)) * fertilized + (1 | site:block),
     data = SAR_block %>% filter(year == 2018)))
summary(lmer(log(diversity) ~ log(as.numeric(samp_effort)) * fertilized + (1 | site:block),
     data = SAR_block %>% filter(year == 2019)))

ggsave("../Figures/Fig3_sars.pdf",
       p3,
       height = 4.5,
       width = 7)
```

```{r}
# Difference between fertilization / control accumulation curves on the log-log scale
net_diff_long <- sitelabels %>% 
  inner_join(q0_rand, by = c("plot" = "plotno", "site" = "site", "block" = "blockno")) %>%
  select(-sitename, -dateestablished) %>%
  pivot_longer(cols = - c('site', 'block', 'plot', 'fertilized', 'year', 'perm'),
               names_to = 'samples') %>%
  mutate(samples = gsub("X", "", samples)) %>%
  select(-plot) %>%
  mutate(fertilized = if_else(fertilized == 0, 'unfert', 'fert')) %>%
  pivot_wider(values_from = 'value',
              names_from = 'fertilized') %>%
  mutate(diff = log(fert) - log(unfert))

net_diff_byblock <- net_diff_long %>% 
  group_by(perm, year, samples, block, site) %>%
  summarise(mean_diff = mean(as.numeric(diff))) %>%
  group_by(year, samples, block, site) %>%
  summarise(diff_med = quantile(as.numeric(mean_diff), p = 0.5),
            diff_lo = quantile(as.numeric(mean_diff), p = 0.025),
            diff_hi = quantile(as.numeric(mean_diff), p = 1 - .025)) %>%
  arrange(year, as.numeric(samples))
 
net_diff_summary <- net_diff_long %>% 
  group_by(perm, year, samples) %>%
  summarise(diff = mean(diff)) %>%
  group_by(year, samples) %>%
  summarise(diff_med = quantile(diff, p = 0.5),
            diff_lo = quantile(diff, p = 0.00078125),
            diff_hi = quantile(diff, p = 1 - 0.00078125)) %>%
  arrange(year, as.numeric(samples))


diff_spat_byblock <- q0_spat %>%
  select(-sitename, -dateestablished) %>%
  pivot_longer(-c("site", "year", "fertilized", "block", "plot"),
               names_to = "samples",
               values_to = "diversity") %>%
  mutate(samples = gsub("X", "", samples)) %>%
  select(-plot) %>%
  mutate(fertilized = if_else(fertilized == 0, 'unfert', 'fert')) %>%
  pivot_wider(values_from = 'diversity',
              names_from = 'fertilized') %>%
  mutate(diff = log(fert) - log(unfert))

diff_spat <- diff_spat_byblock %>%
  group_by(year, samples) %>%
  summarise(diff = mean(diff))
  
# Total deviance

net_diff_summary %>%
  ggplot(aes(x = as.numeric(samples),
             y = diff_med)) +
  geom_line() +
  geom_ribbon(aes(ymin = diff_lo,
                  ymax = diff_hi)) + 
  geom_line(data = diff_spat,
            aes(y = diff),
            color = "red") +
  facet_wrap(~year)

# Plotting
toplot_byblock <- diff_spat_byblock %>% 
  left_join(net_diff_byblock)

toplot_byyear <- diff_spat %>%
  left_join(net_diff_summary)

# Net Effects Plot
comp_plot <- toplot_byblock %>%
  filter(year == 2019) %>%
  ggplot(aes(x = log(as.numeric(samples)))) +
  geom_ribbon(data = toplot_byyear %>% filter(year == 2019),
            aes(ymin = diff_lo,
                ymax = diff_hi),
            alpha = .2,
            color = 'black') +
  geom_hline(yintercept = 0) +
  geom_line(data = toplot_byyear %>% filter(year == 2019),
            aes(y = diff_med),
            color = "black",
            linetype = 2,
            size = 1.25) +
  geom_line(data = toplot_byyear %>% filter(year == 2019),
            aes(y = diff),
            color = "black",
            size = 1.25) +
  geom_line(aes(y = diff,
                color = site,
                group = paste(site, block)),
            alpha = .5) +
  theme_bw() +
  ylab("Log Response Ratio ") +
  xlab("log(Number of Samples)") +
  scale_color_manual(name = 'Site',
                     values = c("#009E73", "orange3")) +
  ggtitle("a) Richness Response - 2019")
```

```{r}
# Net Effects Plot
aggplot <- toplot_byblock %>%
  filter(year == 2019) %>%
  ggplot(aes(x = log(as.numeric(samples)))) +
  geom_ribbon(data = toplot_byyear %>% filter(year == 2019),
            aes(ymin = diff_lo - diff_med,
                ymax = diff_hi - diff_med),
            alpha = .2,
            color = "black") +
  geom_hline(yintercept = 0) +
  geom_line(aes(y = diff - diff_med,
                color = site,
                group = paste(site, block)),
            alpha = .5) +
  geom_line(data = toplot_byyear %>% filter(year == 2019),
            aes(y = diff - diff_med),
            color = "black",
            size = 1.25) +
  theme_bw() +
  ylab("Net Effect of Aggregation") +
  xlab("log(Number of Samples)") +
  scale_color_manual(name = 'Site',
                     values = c("#009E73", "orange3")) +
  ggtitle("b) Aggregation Effect - 2019")

g_legend<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)}

mylegend<-g_legend(aggplot)

p3 <- arrangeGrob(arrangeGrob(comp_plot + theme(legend.position="none"),
                         aggplot + theme(legend.position="none"),
                         nrow=1),
             mylegend, nrow=1,widths =c(6, 1))

ggsave("../Figures/Fig5_aggeffects.pdf",
       p3,
       height = 4,
       width = 8)
```

```{r}
comp2018 <- toplot_byblock %>%
  filter(year == 2018) %>%
  ggplot(aes(x = log(as.numeric(samples)))) +
  geom_ribbon(data = toplot_byyear %>% filter(year == 2018),
            aes(ymin = diff_lo,
                ymax = diff_hi),
            alpha = .2,
            color = 'black') +
  geom_hline(yintercept = 0) +
  geom_line(data = toplot_byyear %>% filter(year == 2018),
            aes(y = diff_med),
            color = "black",
            linetype = 2,
            size = 1.25) +
  geom_line(data = toplot_byyear %>% filter(year == 2018),
            aes(y = diff),
            color = "black",
            size = 1.25) +
  geom_line(aes(y = diff,
                color = site,
                group = paste(site, block)),
            alpha = .5) +
  theme_bw() +
  ylab("Log Response Ratio ") +
  xlab("log(Number of Samples)") +
  scale_color_manual(name = 'Site',
                     values = c("#009E73", "orange3")) +
  ggtitle("a) Richness Response - 2018")


comp2017 <- toplot_byblock %>%
  filter(year == 2017) %>%
  ggplot(aes(x = log(as.numeric(samples)))) +
  geom_ribbon(data = toplot_byyear %>% filter(year == 2017),
            aes(ymin = diff_lo,
                ymax = diff_hi),
            alpha = .2,
            color = 'black') +
  geom_hline(yintercept = 0) +
  geom_line(data = toplot_byyear %>% filter(year == 2017),
            aes(y = diff_med),
            color = "black",
            linetype = 2,
            size = 1.25) +
  geom_line(data = toplot_byyear %>% filter(year == 2017),
            aes(y = diff),
            color = "black",
            size = 1.25) +
  geom_line(aes(y = diff,
                color = site,
                group = paste(site, block)),
            alpha = .5) +
  theme_bw() +
  ylab("Log Response Ratio ") +
  xlab("log(Number of Samples)") +
  scale_color_manual(name = 'Site',
                     values = c("#009E73", "orange3")) +
  ggtitle("a) Richness Response - 2017")

agg2018 <- toplot_byblock %>%
  filter(year == 2018) %>%
  ggplot(aes(x = log(as.numeric(samples)))) +
  geom_ribbon(data = toplot_byyear %>% filter(year == 2018),
            aes(ymin = diff_lo - diff_med,
                ymax = diff_hi - diff_med),
            alpha = .2,
            color = 'black') +
  geom_line(aes(y = diff - diff_med,
                color = site,
                group = paste(site, block)),
            alpha = .5) +
  geom_line(data = toplot_byyear %>% filter(year == 2018),
            aes(y = diff - diff_med),
            color = "black",
            size = 1.5) +
  theme_bw() +
  ylab("Net Effect of Aggregation") +
  xlab("Number of Samples") +
  scale_color_manual(name = 'Site',
                     values = c("#009E73", "orange3")) +
  ggtitle("b) Aggregation Effect - 2018")

agg2017 <- toplot_byblock %>%
  filter(year == 2017) %>%
  ggplot(aes(x = log(as.numeric(samples)))) +
  geom_ribbon(data = toplot_byyear %>% filter(year == 2017),
            aes(ymin = diff_lo - diff_med,
                ymax = diff_hi - diff_med),
            alpha = .2,
            color = 'black') +
  geom_line(aes(y = diff - diff_med,
                color = site,
                group = paste(site, block)),
            alpha = .5) +
  geom_line(data = toplot_byyear %>% filter(year == 2017),
            aes(y = diff - diff_med),
            color = "black",
            size = 1.5) +
  theme_bw() +
  ylab("Net Effect of Aggregation") +
  xlab("Number of Samples") +
  scale_color_manual(name = 'Site',
                     values = c("#009E73", "orange3")) +
  ggtitle("b) Aggregation Effect - 2017")



p3 <- arrangeGrob(arrangeGrob(comp2018 + theme(legend.position="none"),
                         agg2018 + theme(legend.position="none"),
                         nrow=1),
             mylegend, nrow=1,widths =c(6, 1))

ggsave("../Figures/supp2018_aggeffects.pdf",
       p3,
       height = 4,
       width = 8)


p3 <- arrangeGrob(arrangeGrob(comp2017 + theme(legend.position="none"),
                         agg2017 + theme(legend.position="none"),
                         nrow=1),
             mylegend, nrow=1,widths =c(6, 1))

ggsave("../Figures/supp2017_aggeffects.pdf",
       p3,
       height = 4,
       width = 8)
```






```{r}
rand_forviz <- sitelabels %>% 
  inner_join(q0_rand, by = c("plot" = "plotno", "site" = "site", "block" = "blockno")) %>%
  select(-sitename, -dateestablished) %>%
  pivot_longer(cols = - c('site', 'block', 'plot', 'fertilized', 'year', 'perm'),
               names_to = 'samples') %>%
  mutate(samples = gsub("X", "", samples)) %>%
  select(-plot) %>%
  mutate(fertilized = if_else(fertilized == 0, 'unfert', 'fert')) %>%
  group_by(site, block, fertilized, year, samples) %>%
  summarise(diversity = median(value),
            diff_lo = quantile(value, p = 0.00078125),
            diff_hi = quantile(value, p = 1 - 0.00078125)) %>%
  arrange(site, block, year, fertilized, as.numeric(samples))

spat_forviz <- q0_spat %>%
  select(-sitename, -dateestablished) %>%
  pivot_longer(-c("site", "year", "fertilized", "block", "plot"),
               names_to = "samples", 
               values_to = "diversity") %>%
  mutate(samples = gsub("X", "", samples)) %>%
  select(-plot) %>%
  mutate(fertilized = if_else(fertilized == 0, 'unfert', 'fert'))

ggplot(aes(x = log(as.numeric(samples)),
           y = log(diversity),
           color = fertilized),
       data = rand_forviz %>% filter(year == 2019)) +
  theme_bw() +
  # geom_ribbon(data = rand_forviz %>% filter(year == 2019),
  #             aes(ymin = log(diff_lo),
  #                 ymax = log(diff_hi),
  #                 fill = fertilized),
  #             alpha = .2) +
  geom_line(data = rand_forviz %>% filter(year == 2019),
            linetype = 3, size = 1.25) +
  geom_line(data = spat_forviz %>% filter(year == 2019),
             size = 1.25) +
  facet_grid(site ~ block) +
  scale_color_manual(name = 'Treatment',
                    labels = c('Control', '+N'),
                    values = c("#357EBDFF", "#D43F3AFF")) +
  scale_fill_manual(name = 'Treatment',
                    labels = c('Control', '+N'),
                    values = c("#357EBDFF", "#D43F3AFF")) +
  ylab("Log(Species Richness)") +
  xlab("Log(Number of Samples)") +
  ggtitle("Spatial and Nonspatial Rarefaction - 2019")

ggsave("../Figures/supp2019_rarecurves.pdf",
       height = 4,
       width = 8)

ggplot(aes(x = log(as.numeric(samples)),
           y = log(diversity),
           color = fertilized),
       data = rand_forviz %>% filter(year == 2018)) +
  theme_bw() +
  # geom_ribbon(data = rand_forviz %>% filter(year == 2018),
  #             aes(ymin = log(diff_lo),
  #                 ymax = log(diff_hi),
  #                 fill = fertilized),
  #             alpha = .2) +
  geom_line(data = rand_forviz %>% filter(year == 2018),
            linetype = 3, size = 1.25) +
  geom_line(data = spat_forviz %>% filter(year == 2018),
             size = 1.25) +
  facet_grid(site ~ block) +
  scale_color_manual(name = 'Treatment',
                    labels = c('Control', '+N'),
                    values = c("#357EBDFF", "#D43F3AFF")) +
  scale_fill_manual(name = 'Treatment',
                    labels = c('Control', '+N'),
                    values = c("#357EBDFF", "#D43F3AFF")) +
  ylab("Log(Species Richness)") +
  xlab("Log(Number of Samples)") +
  ggtitle("Spatial and Nonspatial Rarefaction - 2018")

ggsave("../Figures/supp2018_rarecurves.pdf",
       height = 4,
       width = 8)

ggplot(aes(x = log(as.numeric(samples)),
           y = log(diversity),
           color = fertilized),
       data = rand_forviz %>% filter(year == 2017)) +
  theme_bw() +
  # geom_ribbon(data = rand_forviz %>% filter(year == 2017),
  #             aes(ymin = log(diff_lo),
  #                 ymax = log(diff_hi),
  #                 fill = fertilized),
  #             alpha = .2) +
  geom_line(data = rand_forviz %>% filter(year == 2017),
            linetype = 3, size = 1.25) +
  geom_line(data = spat_forviz %>% filter(year == 2017),
             size = 1.25) +
  facet_grid(site ~ block) +
  scale_color_manual(name = 'Treatment',
                    labels = c('Control', '+N'),
                    values = c("#357EBDFF", "#D43F3AFF")) +
  scale_fill_manual(name = 'Treatment',
                    labels = c('Control', '+N'),
                    values = c("#357EBDFF", "#D43F3AFF")) +
  ylab("Log(Species Richness)") +
  xlab("Log(Number of Samples)") +
  ggtitle("Spatial and Nonspatial Rarefaction - 2017")

ggsave("../Figures/supp2017_rarecurves.pdf",
       height = 4,
       width = 8)
```












```{r}
q2_spat <- inner_join(sitelabels, q2_spat, by = c("plot" = "plotno", "site" = "site", "block" = "blockno"))

q2_spat %>% group_by(year, fertilized) %>% summarise_if(is.numeric, mean) %>%
  pivot_longer(-c("year", "fertilized", "block", "plot"),
               names_to = "samp_effort",
               values_to = "diversity") %>%
  ggplot(aes(x = log(as.numeric(samp_effort)),
             y = log(diversity),
             color = as.factor(fertilized))) +
  geom_line(size = 1.5) +
  xlab("Log Sampling Effort") +
  ylab("Log Inv. Simpson Diversity") +
  scale_color_discrete(name = "Treatment", labels = c("Control", "Fert")) +
  facet_wrap(~year) +
  ggtitle("Scaling Relationships -- Inv. Simpson Div")

ggsave("../Figures/accum_q2_2019.jpeg", height = 3, width = 6)
```

```{r}
q0_rand <- inner_join(sitelabels, q0_rand, by = c("plot" = "plotno", "site" = "site", "block" = "blockno"))
q0_rand$block <- as.factor(q0_rand$block)
q0_rand$plot <- as.factor(q0_rand$plot)
q0_rand$fertilized <- as.factor(q0_rand$fertilized)
q0_perm_summary <- q0_rand %>% pivot_longer(-c("site", "sitename", "dateestablished", "block", "plot", "fertilized", "year", "permute_iter", "strata"),
                         names_to = "effort",
                         values_to = "diversity") %>%
  select(-plot) %>%
  pivot_wider(id_cols = c("site", "sitename", "dateestablished", "block", "year", "permute_iter", "strata", "effort"),
              names_from = "fertilized",
              names_prefix = "fert",
              values_from = "diversity") %>%
  mutate(diff = fert0 - fert1) %>%
  select(-strata, -dateestablished)

q0_quantiles_byblock <- q0_perm_summary %>%
  group_by(site, block, year, effort) %>%
  summarise(diff_lo = quantile(diff, probs = 0.025),
            diff_mid = quantile(diff, probs = 0.75),
            diff_hi = quantile(diff, probs = 0.975)) %>%
  arrange(as.numeric(effort)) %>%
  ungroup()

q0_quantiles_byyear <- q0_quantiles_byblock %>%
  select(-block) %>%
  group_by(year, effort) %>%
  summarise_if(is.numeric, mean)  %>%
  arrange(year, as.numeric(effort))

q0_quantiles_byyear %>%
  ggplot(aes(x = as.numeric(effort))) +
  geom_ribbon(aes(ymin = diff_lo - diff_mid,
                  ymax = diff_hi - diff_mid)) +
  facet_wrap(~year) +
  geom_line(aes(x = as.numeric(effort),
                y = as.numeric(diff) - diff_mid),
            data = q0_spatvals)

q0_spatvals <- q0_spat %>% group_by(year, fertilized) %>%
  pivot_longer(-c("year", "fertilized", "block", "plot"),
               names_to = "samp_effort",
               values_to = "diversity") %>%
  select(-plot, -block) %>%
  mutate(fertilized = if_else(fertilized == 1, "fert", "unfert")) %>%
  pivot_wider(names_from = fertilized,
              values_from = diversity) %>%
  mutate(diff = unfert - fert)
```

```{r}
q0_spatvals <- q0_spat %>% pivot_longer(-c("site", "sitename", "dateestablished", "block", "plot", "fertilized", "year",  "strata"),
                         names_to = "effort",
                         values_to = "diversity") %>%
  select(-plot) %>%
  pivot_wider(id_cols = c("site", "sitename", "dateestablished", "block", "year", "strata", "effort"),
              names_from = "fertilized",
              names_prefix = "fert",
              values_from = "diversity") %>%
  mutate(diff = fert0 - fert1) %>%
  select(-strata, -dateestablished) %>%
  select(-block) %>%
  group_by(year, effort) %>%
  summarise_if(is.numeric, mean) %>%
  arrange(year, as.numeric(effort))
```


