---
title: "Accumulation Curve Fitting"
output: html_notebook
---

The next step in this analysis is to examine how these effects differ as a function
of the number of samples included -- are effects strongest locally and linearly
decline? Or do they show a nonlinear pattern? How important are spatial distributions?  

Here, I generate accumulation curves for each plot to capture these effects. The 
first approach, the "empirical" accumulation curve captures the effects of both
plot community composition and spatial distribution. The second, the "random" accumulation
curve, randomizes plot positions to remove these spatial effects, and can serve 
as a null model.

## Loading in datasets

```{r}

# Community data

# Community matrix attributes

```

## Loading Functions

```{r}
source("diversity_metrics.R")
source("gamma_permutation.R")
source("test_diversity_metrics.R")
```

---

## Accumulation at q = 0

### Generating empirical accumulation curves


### Generating a list of randomized accumulation curves


### Visualization

Observed diversity difference as a function of scale

* 3 lines, one per year, of average difference between curves? Proportional?

Spatial effect contribution as a function of scale

* Observed vs. null model. Associated significance?

Decomposition of effects as a function of 


---

## Accumulation at q = 2

### Generating empirical accumulation curves


### Generating a list of randomized accumulation curves
