---
title: "Biomass and Light Analysis"
output: html_notebook
---

```{r}
library(tidyverse);library(lme4);library(lmerTest);library(emmeans);
library(grid);library(gridExtra);library(boot)
```


# Reading in datasets

```{r}
sitelabels <- read.csv(file = "../Data/FinalDatasets/Site_Descriptions.csv")
head(sitelabels)

bmass <- read.csv(file = "../Data/FinalDatasets/Biomass_Final.csv")
head(bmass)

light <- read.csv(file = "../Data/FinalDatasets/Light_Final.csv")
head(light)

# Filtering to SFREC and MCLA

bmass <- bmass %>% filter(site != "HREC") %>%
  left_join(sitelabels, on = list("site" = "site",
                                  "block" = "block",
                                  "plot" = "plot"))


light <- light %>% filter(site != "HREC") %>%
  left_join(sitelabels, on = list("site" = "site",
                                  "block" = "block",
                                  "plot" = "plot"))

```

---

# Light data

Statistics of interest:

#### Total light interception (1 - light availability)  
Average of two samples divided by the proportion available at surface

#### Heterogeneity of light interception 
Coefficient of variation of light availability

## Model fitting:

Mixed model predicting light as a function of the years of treatment, with random effects accounting for the repeated measurements within each block

$$Light = factor(Year) * factor(Treatment) + (1 | Block:Site)$$

```{r}
colnames(light)

mod_light_full <- lmer(Interception ~ as.factor(year) * as.factor(fertilized) + (1 | block:site) ,
     data = light)

mod_light_add <- lmer(Interception ~ as.factor(year) + as.factor(fertilized) + (1 | block:site),
     data = light)

anova(mod_light_full) # No significant deviations

summary(mod_light_add)

library(emmeans)
emmeans(mod_light_full, pairwise ~ fertilized|year, adjust = "bonferroni", lmer.df = "satterthwaite")

# Diagnostics

plot(mod_light_add) # Check resid

light[order(abs(resid(mod_light_add)), decreasing = TRUE),] # Check cell 480 in master datasheet

bootfunction <- function(dat,i){
  mod <- lmer(Interception ~ as.factor(year) * as.factor(fertilized) + (1 | block:site), data = dat[i,])
  coefs <- fixef(mod)
  return(c(coefs[1],
         coefs[1] + coefs[4],
         coefs[1] + coefs[2],
         coefs[1] + coefs[2] + coefs[4] + coefs[5],
         coefs[1] + coefs[3],
         coefs[1] + coefs[3] + coefs[4] + coefs[6]))
}

fixef(mod_light_full)
light_boots <- boot(light, statistic = bootfunction, R = 9999)

bootcis <- data.frame(
  matrix(
    c(boot.ci(light_boots,type="perc", index = 1, conf = 1 - (.05 / 3))$percent[c(4,5)],
      boot.ci(light_boots,type="perc", index = 2, conf = 1 - (.05 / 3))$percent[c(4,5)],
      boot.ci(light_boots,type="perc", index = 3, conf = 1 - (.05 / 3))$percent[c(4,5)],
      boot.ci(light_boots,type="perc", index = 4, conf = 1 - (.05 / 3))$percent[c(4,5)],
      boot.ci(light_boots,type="perc", index = 5, conf = 1 - (.05 / 3))$percent[c(4,5)],
      boot.ci(light_boots,type="perc", index = 6, conf = 1 - (.05 / 3))$percent[c(4,5)]),
    ncol = 2, byrow = TRUE))

colnames(bootcis) = c("low", "high")

```


### Visualization of model fit

Net difference between 

```{r}
bygroup <- light %>%
  group_by(year, site, block, fertilized) %>%
  summarise(mean_int = mean(Interception),
            se_interception = sd(Interception) / sqrt(n()))

byyear <- light %>%
  group_by(year, fertilized) %>%
  summarise(mean_int = mean(Interception)) %>%
  bind_cols(bootcis)
```

```{r}
light_plot <- ggplot() +
  geom_point(aes(x = as.factor(year),
                 y = mean_int,
                 fill = as.factor(fertilized)),
             shape = 21,
             data = bygroup,
             alpha = .5,
             size = 2,
             position = position_dodge(width = .5)) +
  geom_errorbar(aes(x = as.factor(year),
                 ymin = low,
                 ymax = high,
                 color = as.factor(fertilized)),
             data = byyear,
             width = .1,
             size = 1.2,
             position = position_dodge(width = .5)) +
  geom_point(aes(x = as.factor(year),
                 y = mean_int,
                 fill = as.factor(fertilized)),
             shape = 21,
             data = byyear,
             size = 6,
             position = position_dodge(width = .5)) +
  ylab("Total PAR Intercepted (%)") +
  xlab("Year") +
  scale_fill_manual(name = 'Treatment',
                    labels = c('Control', '+N'),
                    values = c("#357EBDFF", "#D43F3AFF")) +
  scale_color_manual(name = 'Treatment',
                    labels = c('Control', '+N'),
                    values = c("black", "black")) +
  ggtitle("b) Light Interception") +
  theme_bw()
```

---

# Biomass data

Statistics of interest:

#### Total community biomass
Biomass (g) / .1m^2

#### Heterogeneity of biomass
Coefficient of variation of biomass availability

## Model fitting:

Mixed model predicting biomass as a function of the years of treatment, with random effects accounting for the non-random effects of block. Sampling locations were randomized, so a random effect of plot was not included.

$$Biomass = factor(Year_{trt}) + (1 | Block)$$

```{r}
head(bmass)

mod_bmass_full <- lmer(Total.Biomass ~ as.factor(year) * as.factor(fertilized) + (1 | site:block),
             data = bmass)

mod_bmass_add <- lmer(Total.Biomass ~ as.factor(year) + as.factor(fertilized) + (1 | site:block),
             data = bmass)

anova(mod_bmass_full, mod_bmass_add)

anova(mod_bmass_full)

bootfunction <- function(dat,i){
  mod <- lmer(Total.Biomass ~ as.factor(year) * as.factor(fertilized) + (1 | site:block), data = dat[i,])
  coefs <- fixef(mod)
  return(c(coefs[1],
         coefs[1] + coefs[4],
         coefs[1] + coefs[2],
         coefs[1] + coefs[2] + coefs[4] + coefs[5],
         coefs[1] + coefs[3],
         coefs[1] + coefs[3] + coefs[4] + coefs[6]))
}

light_boots <- boot(bmass, statistic = bootfunction, R = 9999)

bootcis <- data.frame(
  matrix(
    c(boot.ci(light_boots,type="perc", index = 1, conf = 1 - (.05 / 3))$percent[c(4,5)],
      boot.ci(light_boots,type="perc", index = 2, conf = 1 - (.05 / 3))$percent[c(4,5)],
      boot.ci(light_boots,type="perc", index = 3, conf = 1 - (.05 / 3))$percent[c(4,5)],
      boot.ci(light_boots,type="perc", index = 4, conf = 1 - (.05 / 3))$percent[c(4,5)],
      boot.ci(light_boots,type="perc", index = 5, conf = 1 - (.05 / 3))$percent[c(4,5)],
      boot.ci(light_boots,type="perc", index = 6, conf = 1 - (.05 / 3))$percent[c(4,5)]),
    ncol = 2, byrow = TRUE))

colnames(bootcis) = c("low", "high")

```

### Visualization of model fit

```{r}
bygroup <- bmass %>%
  group_by(year, site, block, fertilized) %>%
  summarise(mean_mass = mean(na.omit(Total.Biomass)),
            se_mass = sd(na.omit(Total.Biomass)) / sqrt(n()))

byyear <- bmass %>%
  group_by(year, fertilized) %>%
  summarise(mean_mass = mean(na.omit(Total.Biomass))) %>%
  bind_cols(bootcis)

bootfunction(bmass)
byyear$mean_mass <- bootfunction(bmass)
```

```{r}
bmass_plot <- ggplot() +
  geom_point(aes(x = as.factor(year),
                 y = mean_mass * 10,
                 fill = as.factor(fertilized)),
             shape = 21,
             data = bygroup,
             alpha = .5,
             size = 2,
             position = position_dodge(width = .5)) +
      geom_errorbar(aes(x = as.factor(year),
                 ymin = low * 10,
                 ymax = high * 10,
                 color = as.factor(fertilized)),
             data = byyear,
             width = .1,
             size = 1.2,
             position = position_dodge(width = .5)) +
  geom_point(aes(x = as.factor(year),
                 y = mean_mass * 10,
                 fill = as.factor(fertilized)),
             shape = 21,
             data = byyear,
             size = 6,
             position = position_dodge(width = .5)) +
  ylab("Total Biomass (g / m^2)") +
  xlab("Year") +
  scale_fill_manual(name = 'Treatment',
                    labels = c('Control', '+N'),
                    values = c("#357EBDFF", "#D43F3AFF")) +
  scale_color_manual(name = 'Treatment',
                    labels = c('Control', '+N'),
                    values = c("black", "black")) +
  ggtitle("a) Biomass") +
  theme_bw()
```

```{r}
g_legend<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)}

mylegend<-g_legend(bmass_plot)

p3 <- arrangeGrob(arrangeGrob(bmass_plot + theme(legend.position="none"),
                         light_plot + theme(legend.position="none"),
                         nrow=1),
             mylegend, nrow=1,widths =c(6, 1))

ggsave("../Figures/Fig2_lightprod.pdf",
       p3,
       height = 4.5,
       width = 8)
```

