---
title: "Biomass and Light Analysis"
output: html_notebook
---

# Reading in datasets

```{r}

```

---

# Light data

Statistics of interest:

#### Total light interception (1 - light availability)  
Average of two samples divided by the proportion available at surface

#### Heterogeneity of light interception 
Coefficient of variation of light availability

## Model fitting:

Mixed model predicting light as a function of the years of treatment, with random effects accounting for the non-random effects of block and repeated observation of plot.

$$Light = factor(Year_{trt}) + (1 | Block) + (1 | Block : Plot)$$

```{r}

# Diagnostics

```


### Comparison with other model types:

```{r}

```

### Visualization of model fit

Predicted means across all sites

---

# Biomass data

Statistics of interest:

#### Total community biomass
Biomass (g) / .1m^2

#### Heterogeneity of biomass
Coefficient of variation of biomass availability

## Model fitting:

Mixed model predicting biomass as a function of the years of treatment, with random effects accounting for the non-random effects of block. Sampling locations were randomized, so a random effect of plot was not included.

$$Biomass = factor(Year_{trt}) + (1 | Block)$$

```{r}

# Diagnostics

```


### Comparison with other model types:

```{r}

```

### Visualization of model fit

Predicted means across all sites






