---
title: "Combining Datasets by Year"
output:
  html_document:
    df_print: paged
---

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)

# 2017 Community data
data2017 <- read.csv("../2017/alldatacombined2017.csv", stringsAsFactors = FALSE)

# 2018 Community data
data2018 <- read.csv("../2018/merged_data_2018_final.csv", stringsAsFactors = FALSE)

# Site descriptions
descriptions <- read.csv("../2017/SiteDescriptions.csv")

# Species labels
specs <- read.csv("../SpeciesList.csv")

# Renames columns to be consistent
colnames(data2017)[1:7] <- c("site", "block", "plot", "subplot", "x", "y", "note")
colnames(data2018)[1:7] <- c("index", "site", "block", "plot", "subplot", "x", "y")

# Turning labels to all lowercase
colnames(data2017) <- tolower(colnames(data2017))
colnames(data2018) <- tolower(colnames(data2018))

# Adding year column
data2017$year <- rep(2017, nrow(data2017))
data2018$year <- rep(2018, nrow(data2018))

# Converting species labels to all lowercase
specs$Label <- tolower(specs$Label)

# Checking that all column names are present
colnames(data2018)[!colnames(data2018) %in% specs$Label]
colnames(data2017)[!colnames(data2017) %in% specs$Label]

# Changing "MCL" to "MCLA"
data2017$site <- gsub("MCL", "MCLA", data2017$site)


master <- bind_rows(data2017, data2018)
table(master %>% select(site, block, plot, year))
```

# Next steps:

* Standardize list of species among groups
* Check for errors
  * Some easy ones:
      * No medicago polymorpha? Just Trifolium dubium $\checkmark$
      * VicVil vs. VicSat (VicSat only @ Hopland?)
      * What is V1
      * Spiky hypochaeris vs. notago $\checkmark$
      *__Tolpis barbata__*
      * Removing question marks from certain species
      * Tritileia blue to Trilieia laxa $\checkmark$
  * Make sure unite is not taking two columns together, but instead, the highest value $\checkmark$

```{r}
com.mat <- master %>% 
  select(- one_of("site", "block", "plot", "subplot", "x", "y", "note", "index", "year")) 
 com.attr <-  master %>% 
   select(one_of("site", "block", "plot", "subplot", "x", "y", "note", "index", "year"))

# Converting NAs to zeroes
com.mat[is.na(com.mat)] <- 0

# Subsetting to just live species 
livespecs <- specs[specs$Live == 1,]
com.mat <- com.mat %>% select(one_of(as.character(livespecs$Label)))

# For each of these labels, rename to the correct species label and unite shared columns
# Can likely reuse old script for this

col_labs <- livespecs[unlist(lapply(livespecs[,1], FUN=function(x){x %in% colnames(com.mat)})),]
```

```{r}
clean_dat <- com.attr

for(colname in unique(col_labs$Species)){
  
  oldcols = col_labs$Label[col_labs$Species == colname]
  oldcols = as.character(oldcols)

  toadd = com.mat %>% 
    select(one_of(oldcols))
  
  toadd = apply(toadd, 1, FUN = function(x){return(max(as.numeric(x)))})
  toadd = data.frame(toadd)
  names(toadd) = colname
  
  clean_dat <- clean_dat %>% bind_cols(toadd)
}

colorder <- c(colnames(clean_dat)[1:9], 
              sort(colnames(clean_dat)[10:length(colnames(clean_dat))]))

final_merged <- clean_dat
final_merged <- final_merged %>% arrange(year, site, block, plot, y, x)
```

# Looking at the abundance of VicSat and VicVil at different sites

* Will remove VicSat from MCLA

```{r}
final_merged %>% ggplot(aes(x = block,
                     y = Vicia.villosa,
                     color = year)) +
  geom_jitter() +
  facet_wrap(~site)

final_merged %>% ggplot(aes(x = block,
                     y = Vicia.sativa,
                     color = year)) +
  geom_jitter() +
  facet_wrap(~site)

final_merged$Vicia.sativa[final_merged$site == "MCLA"] = 0
```



```{r}

com.mat <- final_merged %>% select(- one_of("site", "block", "plot", "subplot", "x", "y", "note", "index", "year"))
com.attr <-  final_merged %>% select(one_of("site", "block", "plot", "subplot", "x", "y", "note", "index", "year"))

com.attr <- left_join(com.attr, descriptions, by = c("site", "block", "plot"))

daub_correction <- function(x){
  if(x == 1){ x <- ((0+1)/2)}
  if(x == 2){ x <- ((1+5)/2)}
  if(x == 3){ x <- ((5+25)/2)}
  if(x == 4){ x <- ((25+50)/2)}
  if(x == 5){ x <- ((50+75)/2)}
  if(x == 6){ x <- ((75+95)/2)}
  if(x == 7){ x <- ((95+100)/2)}
  if(x == 0){ x <- 0}
  return(x)
}

com.mat <- apply(com.mat,
                 MARGIN = c(1,2), 
                 FUN = daub_correction)

com.mat <- data.frame(com.mat)

# Checking that all values are as they should be (0, .5, 15, 37.5, 62.5, 85, 97.5)
unique(unlist(com.mat))
```

```{r}
hist(rowSums(com.mat))
final_forstats <- bind_cols(com.attr, com.mat)

head(final_forstats)[,1:20]

write.csv("../final_2018.csv", x = final_forstats)
```

# What are the most abundant species in each site by year?

```{r}
final_forstats %>% 
  select(-one_of("index", "note", "sitename", "dateestablished", "plotlocation")) %>%
  gather(key = "spec", value = "cover", -site, -block, -plot, -subplot, -x, -y, -year, -fertilized) %>%
  group_by(site, block, plot, year, spec, fertilized) %>%
  summarise(specmean = mean(cover)) %>%
  arrange(desc(specmean), .by_group = TRUE) %>%
  top_n(wt = specmean, 15) %>%
  filter(site == "HREC") %>%
  filter(specmean > 5) %>%
  ggplot(aes(x = spec,
             y = specmean,
             color = factor(year),
             shape = factor(fertilized))) +
  geom_point()+
  facet_wrap(~block) + theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  ggtitle("HREC")+
  ylim(0, 70)
```

```{r}
final_forstats %>% 
  select(-one_of("index", "note", "sitename", "dateestablished", "plotlocation")) %>%
  gather(key = "spec", value = "cover", -site, -block, -plot, -subplot, -x, -y, -year, -fertilized) %>%
  group_by(site, block, plot, year, spec, fertilized) %>%
  summarise(specmean = mean(cover)) %>%
  arrange(desc(specmean), .by_group = TRUE) %>%
  top_n(wt = specmean, 15) %>%
  filter(site == "SFREC") %>%
  filter(specmean > 5) %>%
  ggplot(aes(x = spec,
             y = specmean,
             color = factor(year),
             shape = factor(fertilized))) +
  geom_point()+
  facet_wrap(~block) + theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ggtitle("SFREC")+
  ylim(0, 70)
```
```{r}
final_forstats %>% 
  select(-one_of("index", "note", "sitename", "dateestablished", "plotlocation")) %>%
  gather(key = "spec", value = "cover", -site, -block, -plot, -subplot, -x, -y, -year, -fertilized) %>%
  group_by(site, block, plot, year, spec, fertilized) %>%
  summarise(specmean = mean(cover)) %>%
  arrange(desc(specmean), .by_group = TRUE) %>%
  top_n(wt = specmean, 15) %>%
  filter(site == "MCLA") %>%
  filter(specmean > 5) %>%
  ggplot(aes(x = spec,
             y = specmean,
             color = factor(year),
             shape = factor(fertilized))) +
  geom_point()+
  facet_wrap(~block) + theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylim(0,70)+
  ggtitle("MCLA")
```

