---
title: "Data Checking"
author: "Evan Batzer"
date: "March 28, 2020"
output: html_document
---
```{r}
library(tidyverse)

com_data  <- read.csv("../Data/FinalDatasets/Community_Final.csv")

# com_data <- com_data %>% select(-"index")

idcols <- c("site", "blockno", "plotno", "subplotno", "subplotx", "subploty", "year", "index")

com_data <- com_data %>% filter(site %in% c("SFREC", "MCLA"))

com_att <- com_data %>% dplyr::select(all_of(idcols))

com_mat <- com_data %>% dplyr::select(-one_of(idcols))

dim(com_att)
dim(com_mat)
```

### Summarizing to find patterns in abundance, odd species, etc.

Best here will be to write a separate dataset for each of the different sites, then attempt to standardize over each separately.

Should:
  Subset to block within sites
  Remove all columns where no species are recorded
  Output a new dataframe
  
Then:
  Collect and collapse dataframes together
  
\check Done

```{r}
sites <- unique(com_att$site)
blocks <- unique(com_att$blockno)

for(sitename in sites){
  for(blockid in blocks){
   
  com_subset <- com_mat[com_att$site == sitename & com_att$blockno == blockid,]
  att_subset <- com_att[com_att$site == sitename & com_att$blockno == blockid,c(1,2,3,7)]
  com_subset <- com_subset[,colSums(com_subset) > 0]
  
  testthat::expect_equal(nrow(att_subset), nrow(com_subset))
  
  # write.csv(x = cbind(att_subset, com_subset),
  #           file = paste("../Data/CheckMat_",sitename,blockid,".csv", sep = ""))    
  
  colsummary <- cbind(att_subset, com_subset) %>%
    group_by(site, year, blockno, plotno) %>%
    summarise_if(is.numeric, sum) %>%
    pivot_longer(cols = -one_of(c('site', 'year', 'blockno', 'plotno')),
                 names_to = "species", values_to = "cover") %>%
    arrange(species, year, plotno)
  
  # write.csv(x = colsummary,
  #           file = paste("../Data/CheckCols_",sitename,blockid,".csv", sep = ""))    
  }
}
```

# Re-joining fixed datasets

```{r}
rm(newdf)

for(sitename in sites){
  for(blockid in blocks){
    
    filename <- paste("../Data/DataChecking/CheckMat_",sitename,blockid,"_fixed.csv", sep = "")    
    cat(paste(sitename, blockid))
    if(!exists("newdf")){
      newdf <- read_csv(filename)
      colnames(newdf)[1] <- "index"
      cat(sort(colnames(newdf)))
    }else{
      tempdf <- read_csv(filename)
      colnames(tempdf)[1] <- "index"
      newdf <- bind_rows(newdf, tempdf)
      cat(sort(colnames(tempdf)))

    }  
  }
}

finalmat <- newdf[,c(1:5, 5 + order(colnames(newdf)[6:ncol(newdf)]))]
finalmat[is.na(finalmat)] <- 0
finalmat <- finalmat %>% arrange(index)

write.csv(x = cbind(com_att %>% arrange(index), finalmat[,-c(1:5)]),        
          file = "../Data/finalmat_draft.csv")
```