---
title: "Two-Scale Analysis"
output: html_notebook
---

Comparison of alpha, beta, and gamma diversity between plots forms what is commonly 
referred to as a "two-scale" analysis in scaling research, as metrics are constructed 
using the finest spatial resolution (subplots) relative to the largest resolution (plots).  

Of the 3 possible mechanisms that could be responsible for generating our response 
curves, the two-scale analysis focuses on effects purely related to the species 
abundance distribution -- both richness and relative abundance of communities.
Changes in community spatial patterns, which require information on sample XY
coordinates, can't be assessed in this approach, as we can't address anything
below our minimum spatial grain or at the largest possible scale.  

I conduct analysis here using two types of diversity measures that differentially
account for the abundance of different species. Using linearized diversity metrics
(Jost 2006, 2009), weighting species abundances to the power of 0 (q=0) or to the
power of 2 (q=2) focus on richness and "evenness", respectively. 

Comparing effects using these metrics can reveal the mechanism for observed diversity
change -- a common response seems to be a loss of diversity in both metrics at small
scales, but differential effects at larger scales that suggest fertilization rarely
causes local extirpation, but reduces the probability of capturing rare species 
in limited sampling.

## Reading in Datasets

```{r}

```

## Loading Functions

```{r}
source("diversity_metrics.R")
source("gamma_permutation.R")
source("test_diversity_metrics.R")
```


## Visualizing Species Abundance Distributions

Rank-abundance curves for all species at each site, per year (saved for diagnostic
purposes, not shown)

```{r}

```

---

## Two-Scale Analysis, q = 0

### Alpha diversity

### Beta diversity

### Gamma diversity

---

## Two-Scale Analysis, q = 2

### Alpha diversity

### Beta diversity

### Gamma diversity

---

## Visualization

This can be a bit tricky to visualize, so I think the best approach might be to 
focus on either displaying the total lost diversity at each metric, or divide these
values by their mean to produce an estimated effect size (proportion) of biodiversity loss.

### Raw difference in diversity


### Proportional difference in diversity
