---
title: "Two-Scale Analysis"
output: html_notebook
---

Comparison of alpha, beta, and gamma diversity between plots forms what is commonly 
referred to as a "two-scale" analysis in scaling research, as metrics are constructed 
using the finest spatial resolution (subplots) relative to the largest resolution (plots).  

Of the 3 possible mechanisms that could be responsible for generating our response 
curves, the two-scale analysis focuses on effects purely related to the species 
abundance distribution -- both richness and relative abundance of communities.
Changes in community spatial patterns, which require information on sample XY
coordinates, can't be assessed in this approach, as we can't address anything
below our minimum spatial grain or at the largest possible scale.  

I conduct analysis here using two types of diversity measures that differentially
account for the abundance of different species. Using linearized diversity metrics
(Jost 2006, 2009), weighting species abundances to the power of 0 (q=0) or to the
power of 2 (q=2) focus on richness and "evenness", respectively. 

Comparing effects using these metrics can reveal the mechanism for observed diversity
change -- a common response seems to be a loss of diversity in both metrics at small
scales, but differential effects at larger scales that suggest fertilization rarely
causes local extirpation, but reduces the probability of capturing rare species 
in limited sampling.

## Reading in Datasets

```{r}
library(tidyverse);library(data.table); library(grid); library(gridExtra)
library(permute)

# Community data
com_data <- fread("../Data/finalmat_draft.csv")

# Species list
speclist <- read.csv("../Data/SpeciesList.csv")
colnames(speclist)[1] = "Label"

# Treatments
sitelabels <- read.csv(file = "../Data/FinalDatasets/Site_Descriptions.csv")

sitelabels <- sitelabels %>%
              rename(blockno = "block",
                     plotno = "plot")

# Filtering data

com_data <- com_data[,-1] %>% select(-"index")

idcols <- c("site", "blockno", "plotno", "subplotno", "subplotx", "subploty", "year")

com_data <- com_data %>% filter(site %in% c("SFREC", "MCLA"))

com_att <- com_data %>% dplyr::select(all_of(idcols))

com_mat <- com_data %>% dplyr::select(-one_of(idcols)) %>%
  dplyr::select(all_of(speclist$Label[speclist$Include == 1]))

dim(com_att)
dim(com_mat)

# Converting values to cover classes

daub_correction <- function(x){
  if(x == 1){ x <- ((0+1)/2)}
  if(x == 2){ x <- ((1+5)/2)}
  if(x == 3){ x <- ((5+25)/2)}
  if(x == 4){ x <- ((25+50)/2)}
  if(x == 5){ x <- ((50+75)/2)}
  if(x == 6){ x <- ((75+95)/2)}
  if(x == 7){ x <- ((95+100)/2)}
  if(x == 0){ x <- 0}
  return(x)
}

com_mat <- as.data.table(apply(com_mat,
                 MARGIN = c(1,2), 
                 FUN = daub_correction))

which(is.na(com_mat))
# write.csv(x = colnames(com_mat),
#           "../Data/final_columns.csv")

```

---

# Analysis

## Loading Functions

```{r}
source("diversity_metrics.R")
source("gamma_permutation.R")
```


## Visualizing Species Abundance Distributions

Rank-abundance curves for all species at each site, per year (saved for diagnostic
purposes, not shown)

---

```{r}
# Creating split set of matrices
splitmat <- split(com_mat, f = paste(com_att$site, com_att$blockno, com_att$plotno, com_att$year))
splitatt <- split(com_att, f = paste(com_att$site, com_att$blockno, com_att$plotno, com_att$year))

# Saving for future analyses
if(!file_test("-f", "../Data/biodiv_dat.RData")){
  save(com_mat, com_att, splitmat, splitatt, file = "../Data/biodiv_dat.RData")
}
```

## Two-Scale Analysis, q = 0

```{r}
plot_div <- cbind(com_att %>% arrange(site, blockno, plotno, year), 
                  a_q0 = unlist(lapply(splitmat, calculate_alpha_diversity, q = 0)),
                  sn = unlist(lapply(splitmat, function(x) apply(x, specnumber, MARGIN = 1))), # Sanity check
                  a_q2 = unlist(lapply(splitmat, calculate_alpha_diversity, q = 2)),
                  b_q0 = unlist(lapply(splitmat, calculate_beta_diversity, q = 0)),
                  b_q2 = unlist(lapply(splitmat, calculate_beta_diversity, q = 2))) 

block_div <- cbind(distinct(com_att %>% select(site, blockno, plotno, year) %>% arrange(site, blockno, plotno, year)),
                   g_q0 = unlist(lapply(splitmat, calculate_gamma_diversity, q = 0)),
                   g_q2 = unlist(lapply(splitmat, calculate_gamma_diversity, q = 2)))
```

# Summarizing LRRs

```{r}
LRR_summary <- plot_div %>% 
  group_by(year, blockno, plotno, site) %>%
  summarise(mean_alpha_q0 = mean(a_q0),
            mean_alpha_q2 = mean(a_q2),
            mean_beta_q0 = mean(b_q0),
            mean_beta_q2 = mean(b_q2)) %>%
  left_join(sitelabels %>% select(site, blockno, plotno, fertilized)) %>%
  ungroup() %>%
  select(-plotno) %>%
  pivot_wider(names_from = fertilized,
              values_from = -c('year', 'blockno', 'site')) %>%
  group_by(year, blockno, site) %>%
  transmute(LRR_alpha_q0 = mean_alpha_q0_1 / mean_alpha_q0_0,
         LRR_alpha_q2 = mean_alpha_q2_1 / mean_alpha_q2_0,
         LRR_beta_q0 = mean_beta_q0_1 / mean_beta_q0_0,
         LRR_beta_q2 = mean_beta_q2_1 / mean_beta_q2_0)


block_div_summary <- left_join(block_div, sitelabels) %>%
  group_by(year, blockno, plotno, site) %>%
  summarise(mean_gamma_q0 = mean(g_q0),
            mean_gamma_q2 = mean(g_q2)) %>%
  left_join(sitelabels %>% select(site, blockno, plotno, fertilized)) %>%
  ungroup() %>%
  select(-plotno) %>%
  pivot_wider(names_from = fertilized,
              values_from = -c('year', 'blockno', 'site')) %>%
  group_by(year, blockno, site) %>%
  transmute(LRR_gamma_q0 = mean_gamma_q0_1 / mean_gamma_q0_0,
         LRR_gamma_q2 = mean_gamma_q2_1 / mean_gamma_q2_0)

LRR_summary <- left_join(LRR_summary, block_div_summary)

summary(lm(log(LRR_gamma_q2) ~ 0 + as.factor(year), data = LRR_summary))
```

# Bootstrapping

```{r, warnings = FALSE}
n_boots = 9999
output <- list()

for(bootno in 1:n_boots){
  
  samplevec <- c(sample(1:64, size = 64, replace = TRUE))
  while(length(samplevec) < nrow(com_att)){
    samplevec <- c(sample(1:64, size = 64, replace = TRUE), samplevec + 64)
  }
  
  com_mat_boot <- com_mat[samplevec,]
  
  splitmat_boot <- split(com_mat_boot, f = paste(com_att$site, com_att$blockno, com_att$plotno, com_att$year))
  
  block_div <- cbind(distinct(com_att %>% select(site, blockno, plotno, year) %>% 
                                arrange(site, blockno, plotno, year)),
                     g_q0 = unlist(lapply(splitmat_boot, calculate_gamma_diversity, q = 0)),
                     g_q2 = unlist(lapply(splitmat_boot, calculate_gamma_diversity, q = 2)))
  
  plot_div_boot <- plot_div %>% group_by(site, blockno, plotno, year) %>% slice(sample(n(), 64, replace = TRUE))
  
  LRR_summary_boot <- plot_div_boot %>% 
    group_by(site, year, blockno, plotno) %>%
    summarise(mean_alpha_q0 = mean(a_q0),
              mean_alpha_q2 = mean(a_q2),
              mean_beta_q0 = mean(b_q0),
              mean_beta_q2 = mean(b_q2)) %>%
    ungroup() %>%
    left_join(sitelabels %>% select(site, blockno, plotno, fertilized), c("blockno", "plotno", "site")) %>%
    select(-plotno) %>%
    pivot_wider(names_from = fertilized,
                values_from = -c('year', 'blockno', 'site')) %>%
    group_by(year, blockno, site) %>%
    transmute(perm = bootno, 
              LRR_alpha_q0 = mean_alpha_q0_1 / mean_alpha_q0_0,
              LRR_alpha_q2 = mean_alpha_q2_1 / mean_alpha_q2_0,
              LRR_beta_q0 = mean_beta_q0_1 / mean_beta_q0_0,
              LRR_beta_q2 = mean_beta_q2_1 / mean_beta_q2_0)
  
  
  block_div_summary_boot <- left_join(block_div, sitelabels) %>%
    group_by(site, year, blockno, plotno) %>%
    summarise(mean_gamma_q0 = mean(g_q0),
              mean_gamma_q2 = mean(g_q2)) %>%
    ungroup() %>%
    left_join(sitelabels %>% select(site, blockno, plotno, fertilized), c("blockno", "plotno", "site")) %>%
    select(-plotno) %>%
    pivot_wider(names_from = fertilized,
                values_from = -c('year', 'blockno', 'site')) %>%
    group_by(year, blockno, site) %>%
    transmute(LRR_gamma_q0 = mean_gamma_q0_1 / mean_gamma_q0_0,
              LRR_gamma_q2 = mean_gamma_q2_1 / mean_gamma_q2_0)
  
  LRR_summary_boot <- left_join(LRR_summary_boot, block_div_summary_boot, 
                                by = c("year", "blockno", "site"))

  output[[bootno]] <- LRR_summary_boot
}

bootoutput <- bind_rows(output)

bootsummary <- bootoutput %>% group_by(perm, year) %>%
  summarise_if(is.numeric, mean) %>%
  group_by(year) %>%
  summarise_if(is.numeric, quantile, probs = c(.025 / 3, .5, 1 - .025 / 3)) %>%
  mutate(quantile = c(.025, .5, .975))
```



# Visualization

```{r}
LRR_summary_long <- LRR_summary %>%
  pivot_longer(cols = -c('year', 'blockno', 'site'),
               names_to = 'Scale',
               values_to = 'LRR')

LRR_overall <- LRR_summary_long %>%
  group_by(Scale, year) %>%
  summarise(LRR = mean(LRR))

LRR_boots <- bootsummary %>%
  select(-perm, - blockno) %>%
  pivot_longer(cols = -c('year', 'quantile'),
               names_to = 'Scale',
               values_to = 'LRR') %>%
  pivot_wider(values_from = "LRR",
             names_from = "quantile") %>%
  rename('q025' = '0.025',
         'q5' = '0.5',
         'q975' = '0.975')

q0plot <- ggplot(aes(x = as.factor(year),
             y = log(LRR)),
       data = LRR_summary_long[grep('q0', LRR_summary_long$Scale),]) +
  geom_hline(aes(yintercept = 0)) + 
  geom_point(aes(shape = as.factor(site),
                 color = as.factor(site)),
             alpha = .5, size = 2) +
  geom_point(data =  LRR_overall[grep('q0', LRR_overall$Scale),],
             size = 3) +
  geom_errorbar(data = LRR_boots[grep('q0', LRR_boots$Scale),],
                aes(ymin = log(q025),
                    y = log(q5),
                    ymax = log(q975)),
                width = .2,
                size = .5)+
  facet_wrap(~Scale) +
  theme_bw() +
  ylim(-.6, .6) + 
  xlab('Year') +
  ylab('Log Response Ratio') +
  scale_shape_manual(name = 'Site',
                     values = c(15,17)) +
    scale_color_manual(name = 'Site',
                       values = c("#009E73", "orange3"))+
  ggtitle('a) Q = 0')

q2plot <- ggplot(aes(x = as.factor(year),
             y = log(LRR)),
       data = LRR_summary_long[grep('q2', LRR_summary_long$Scale),]) +
  geom_hline(aes(yintercept = 0)) + 
  geom_point(aes(shape = as.factor(site),
                 color = as.factor(site)),
             alpha = .5, size = 2) +
  geom_point(data =  LRR_overall[grep('q2', LRR_overall$Scale),],
             size = 3) +
  geom_errorbar(data = LRR_boots[grep('q2', LRR_boots$Scale),],
                aes(ymin = log(q025),
                    y = log(q5),
                    ymax = log(q975)),
                width = .2,
                size = .5)+
  facet_wrap(~Scale) +
  theme_bw() +
  ylim(-.6, .6) + 
  xlab('Year') +
  ylab('Log Response Ratio') +
  scale_shape_manual(name = 'Site',
                     values = c(15,17)) +
  scale_color_manual(name = 'Site',
                       values = c("#009E73", "orange3"))+
  ggtitle('b) Q = 2')


g_legend<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)}

mylegend<-g_legend(q0plot)

p3 <- arrangeGrob(arrangeGrob(q0plot + theme(legend.position="none"),
                         q2plot + theme(legend.position="none"),
                         nrow=2),
             mylegend, nrow=1,widths =c(6, 1))

ggsave("../Figures/Fig4_twoscale.pdf",
       p3,
       height = 6,
       width = 7)
```

# Changes in occupancy at a local scale

```{r}
presabs <- bind_rows(lapply(splitmat, function(x) colSums(x > 0)))
abunds <- bind_rows(lapply(splitmat, function(x) colSums(x) / 64))

comlabels <- com_att %>% select(site, blockno, plotno, year) %>% unique() %>% arrange(site, blockno, plotno, year)

pres_long <- bind_cols(comlabels, presabs) %>% pivot_longer(-colnames(comlabels),
                                               names_to = "taxon",
                                               values_to = "pres")

abund_long <- bind_cols(comlabels, abunds) %>% pivot_longer(-colnames(comlabels),
                                               names_to = "taxon",
                                               values_to = "abund")

inner_join(pres_long, abund_long) %>%
  left_join(sitelabels %>% select(site, blockno, plotno, fertilized)) %>%
  filter(year == 2019 & pres != 0) %>%
  ggplot(aes(x = log(abund),
             y= pres,
             color = as.factor(fertilized))) +
  geom_point() +
  stat_smooth()
```

```{r}
data_formod <- inner_join(pres_long, abund_long) %>%
  left_join(sitelabels %>% select(site, blockno, plotno, fertilized)) %>%
  filter(pres != 0)
  
summary(glmer(cbind(pres, 64 - pres) ~ log(abund) + fertilized + (1 | blockno:site),
      family = "binomial",
      data = data_formod %>% filter(year == 2017)))

summary(glmer(cbind(pres, 64 - pres) ~ log(abund) + fertilized + (1 | blockno:site),
      family = "binomial",
      data = data_formod %>% filter(year == 2018)))


mod_2019 <- glmer(cbind(pres, 64 - pres) ~ log(abund) + fertilized + (1 | blockno:site),
      family = "binomial",
      data = data_formod %>% filter(year == 2019))
summary(mod_2019)

summary(glmer(cbind(pres, 64 - pres) ~ scale(log(abund)) + as.factor(I(fertilized * year)) + as.factor(year) + (1 | blockno:site) + (1|taxon),
      family = "binomial",
      data = data_formod))
```


```{r}
to_predict <- expand.grid(abund = exp(log(seq(.01, 100, by = .01))),
                       fertilized = c(0,1))
plot_2019 <- cbind(to_predict, 
      pred_occ = predict(mod_2019, newdata = to_predict, re.form = NA, type = "response")) %>%
  ggplot(aes(x = log(abund),
             y = pred_occ,
             color = as.factor(fertilized))) +
  geom_line(size = 1.5) +
  theme_bw() +
  geom_point(aes(y = pres / 64),
             data = data_formod %>% filter(year == 2019),
             alpha = .2) +
  scale_color_manual(name = 'Treatment',
                    labels = c('Control', '+N'),
                    values = c("#357EBDFF", "#D43F3AFF")) +
  xlab('Log(Mean Cover)') +
  ylab('Proportion of Samples Present') +
  ggtitle('2019')



mod_2017 <- glmer(cbind(pres, 64 - pres) ~ log(abund) + fertilized + (1 | blockno:site),
      family = "binomial",
      data = data_formod %>% filter(year == 2017))

to_predict <- expand.grid(abund = exp(log(seq(.01, 100, by = .01))),
                       fertilized = c(0,1))
plot_2017 <- cbind(to_predict, 
      pred_occ = predict(mod_2017, newdata = to_predict, re.form = NA, type = "response")) %>%
  ggplot(aes(x = log(abund),
             y = pred_occ,
             color = as.factor(fertilized))) +
  geom_line(size = 1.5) +
  theme_bw() +
  geom_point(aes(y = pres / 64),
             data = data_formod %>% filter(year == 2017),
             alpha = .2) +
  scale_color_manual(name = 'Treatment',
                    labels = c('Control', '+N'),
                    values = c("#357EBDFF", "#D43F3AFF")) +
  xlab('Log(Mean Cover)') +
  ylab('Proportion of Samples Present') +
  ggtitle('2017')

g_legend<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)}

mylegend<-g_legend(plot_2019)

p3 <- arrangeGrob(arrangeGrob(plot_2017 + theme(legend.position="none"),
                         plot_2019 + theme(legend.position="none"),
                         nrow=1),
             mylegend, top = 'Sample Occupancy vs. Abundance', nrow=1,widths =c(6, 1))

# ggsave("../Figures/Fig6_aggeffects_indiv.pdf",
#        p3,
#        height = 4,
#        width = 8)

```

# Changes in species relative abundances

```{r}
att_block <- distinct(com_att %>% select(site, blockno, plotno, year) %>% arrange(site, blockno, plotno, year)) %>%
  left_join(sitelabels %>% select(site, blockno, plotno, fertilized)) %>%
  mutate(fert_year = (year - 2016) * fertilized)

com_block <- bind_rows(lapply(splitmat, colSums))

mcladat <- com_block[att_block$site == "MCLA",]
mcladat <- mcladat[,colSums(mcladat) > 0]

sfrecdat <- com_block[att_block$site == "SFREC",]
sfrecdat <- sfrecdat[,colSums(sfrecdat) > 0]

library(vegan)

adonis2(mcladat ~ as.factor(blockno) + as.factor(year) + as.factor(fert_year) * as.factor(blockno), 
        data = att_block[att_block$site == "MCLA",])

reducedmod <- adonis(mcladat ~ as.factor(blockno) + as.factor(year), 
        data = att_block[att_block$site == "MCLA",])

nmdsdat <- metaMDS(mcladat^ (1/4), autotransform = FALSE, trymax = 99)
p1 <- cbind(nmdsdat$points, att_block[att_block$site == "MCLA",]) %>%
  ggplot(aes(x = MDS1,
             y = MDS2,
             color = as.factor(year),
             shape = as.factor(fertilized),
             group = paste(year, blockno))) +
  theme_bw()+
  geom_point(size = 3) +
  geom_line() +
  ggrepel::geom_text_repel(aes(label = blockno), show.legend = FALSE) +
  scale_color_discrete(name = "Year") +
  scale_shape_discrete(name = "Treatment", labels = c("Control", "+N")) +
  xlab("NMDS Axis 1") +
  ylab("NMDS Axis 2") +
  ggtitle("Compositional NMDS") +
  geom_text(aes(x = Inf,
                y = -Inf,
                color = NULL,
                shape = NULL,
                group = NULL),
            label = paste("Stress:", round(nmdsdat$stress,2)),
            vjust = -1,
            hjust = 1.5, 
            show.legend = FALSE)

A <- as.matrix((-.5) * vegdist(mcladat) ^ 2, method = "bray")
G <- A - rowMeans(A) + mean(A)
G <- apply(A, MARGIN = 2, FUN = function(x){x - mean(x)})
X <- reducedmod$model.matrix
H <- (X %*% solve(t(X) %*% X) %*% t(X))
sum(diag(as.matrix(G)))

G_r <- (diag(nrow(G)) - H) %*% G %*% (diag(nrow(G)) - H)
sum(diag(G_r))

D_r <- matrix(0, nrow = nrow(G_r), ncol = ncol(G_r))

for(i in c(1:nrow(G_r))){
  
  for(j in c(1:ncol(G_r))){
    D_r[i,j] = sqrt(abs(G_r[i,i] - 2 * G_r[i,j] + G_r[j,j]))
    
  }
}

nmdsdat <- metaMDS(D_r, autotransform = FALSE,trymax = 99)
p2 <- cbind(nmdsdat$points, att_block[att_block$site == "MCLA",]) %>%
  ggplot(aes(x = MDS1,
             y = MDS2,
             color = as.factor(year),
             shape = as.factor(fertilized),
             group = paste(year, blockno))) +
  theme_bw()+
  geom_point(size = 3) +
  # geom_line() +
  ggrepel::geom_text_repel(aes(label = blockno), show.legend = FALSE) +
  scale_color_discrete(name = "Year") +
  scale_shape_discrete(name = "Treatment", labels = c("Control", "+N")) +
  xlab("NMDS Axis 1") +
  ylab("NMDS Axis 2") +
  ggtitle("Residualized NMDS (Year and Block Effects Removed)") +
  geom_text(aes(x = Inf,
                y = -Inf,
                color = NULL,
                shape = NULL,
                group = NULL),
            label = paste("Stress:", round(nmdsdat$stress,2)),
            vjust = -1,
            hjust = 1.5,
            show.legend = FALSE)

g_legend<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)}
mylegend<-g_legend(p2)

p3 <- arrangeGrob(arrangeGrob(p1 + theme(legend.position="none"),
                         p2 + theme(legend.position="none"),
                         nrow=1),
             mylegend,
             top = "McLaughlin UCNRS", nrow=1,widths =c(6, 1))
ggsave("../Figures/appendix_MCLA_NMDS.pdf",
       p3,
       height = 5,
       width = 10)

```

```{r}
taxons <- read.csv('../Data/ColumnIDs_Final.csv')
sfrecdat <- com_block[att_block$site == "SFREC",]
sfrecdat <- sfrecdat[,colSums(sfrecdat) > 0]

adonis2(sfrecdat ~ as.factor(blockno) + as.factor(year) + as.factor(fert_year) * as.factor(blockno), 
        data = att_block[att_block$site == "SFREC",])

reducedmod <- adonis(sfrecdat ~ as.factor(blockno) + as.factor(year), 
        data = att_block[att_block$site == "SFREC",])

nmdsdat <- metaMDS(sfrecdat^ (1/4), autotransform = FALSE)
p1 <- cbind(nmdsdat$points, att_block[att_block$site == "SFREC",]) %>%
  ggplot(aes(x = MDS1,
             y = MDS2,
             color = as.factor(year),
             shape = as.factor(fertilized),
             group = paste(year, blockno))) +
  theme_bw()+
  geom_point(size = 3) +
  geom_line() +
  ggrepel::geom_text_repel(aes(label = blockno)) +
  scale_color_discrete(name = "Year") +
  scale_shape_discrete(name = "Treatment", labels = c("Control", "+N")) +
  xlab("NMDS Axis 1") +
  ylab("NMDS Axis 2") +
  ggtitle("Compositional NMDS") +
  geom_text(aes(x = Inf,
                y = -Inf,
                color = NULL,
                shape = NULL,
                group = NULL),
            label = paste("Stress:", round(nmdsdat$stress,2)),
            vjust = -1,
            hjust = 1.5,
            show.legend = FALSE)

A <- as.matrix((-.5) * vegdist(sfrecdat) ^ 2, method = "bray")
G <- A - rowMeans(A) + mean(A)
G <- apply(A, MARGIN = 2, FUN = function(x){x - mean(x)})
X <- reducedmod$model.matrix
H <- (X %*% solve(t(X) %*% X) %*% t(X))
sum(diag(as.matrix(G)))
sum(diag(G_r))

G_r <- (diag(nrow(G)) - H) %*% G %*% (diag(nrow(G)) - H)

D_r <- matrix(0, nrow = nrow(G_r), ncol = ncol(G_r))

for(i in c(1:nrow(G_r))){
  
  for(j in c(1:ncol(G_r))){
    D_r[i,j] = sqrt(abs(G_r[i,i] - 2 * G_r[i,j] + G_r[j,j]))
    
  }
}

nmdsdat <- metaMDS(D_r, autotransform = FALSE,)
p2 <- cbind(nmdsdat$points, att_block[att_block$site == "SFREC",]) %>%
  ggplot(aes(x = MDS1,
             y = MDS2,
             color = as.factor(year),
             shape = as.factor(fertilized),
             group = paste(year, blockno))) +
  theme_bw()+
  geom_point(size = 3) +
  # geom_line() +
  ggrepel::geom_text_repel(aes(label = blockno)) +
  scale_color_discrete(name = "Year") +
  scale_shape_discrete(name = "Treatment", labels = c("Control", "+N")) +
  xlab("NMDS Axis 1") +
  ylab("NMDS Axis 2")+
  ggtitle("Residualized NMDS (Year and Block Effects Removed)") +
  geom_text(aes(x = Inf,
                y = -Inf,
                color = NULL,
                shape = NULL,
                group = NULL),
            label = paste("Stress:", round(nmdsdat$stress,2)),
            vjust = -1,
            hjust = 1.5,
            show.legend = FALSE)

mylegend<-g_legend(p2)

p3 <- arrangeGrob(arrangeGrob(p1 + theme(legend.position="none"),
                         p2 + theme(legend.position="none"),
                         nrow=1),
             mylegend,
             top = "Sierra Foothill REC", nrow=1,widths =c(6, 1))
ggsave("../Figures/appendix_SFREC_NMDS.pdf",
       p3,
       height = 5,
       width = 10)

```

```{r}
cover_organized <- cbind(att_block[att_block$site == "MCLA", c("site", "fertilized", "blockno", "year")], mcladat) %>%
  arrange(fertilized, blockno, year)
 
net_eff <- (cover_organized[13:24,-c('site', 'fertilized', 'blockno', 'year')] / 
    rowSums(cover_organized[13:24,-c('site', 'fertilized', 'blockno', 'year')])) - 
  (cover_organized[1:12,-c('site', 'fertilized', 'blockno', 'year')] /
     rowSums(cover_organized[1:12,-c('site', 'fertilized', 'blockno', 'year')]))

id_rows <- distinct(cover_organized[,c("site","blockno", "year")])
mean_effects <- cbind(id_rows, net_eff) %>% group_by(site, year) %>% summarise_all(mean) %>% select(-blockno)

control_cov <- (cover_organized[1:12,-c('site', 'fertilized', 'blockno', 'year')] / 
    rowSums(cover_organized[1:12,-c('site', 'fertilized', 'blockno', 'year')]))

mean_control <- cbind(id_rows, control_cov) %>% group_by(site, year) %>% summarise_all(mean) %>% select(-blockno)

cover_summary <- mean_control %>% pivot_longer(cols = -c('site', 'year')) %>%
  pivot_wider(names_from = year,
              values_from = value) %>%
  rename('Cover_2017' = '2017',
         'Cover_2018' = '2018',
         'Cover_2019' = '2019')

effect_summary <- mean_effects %>% pivot_longer(cols = -c('site', 'year')) %>%
  pivot_wider(names_from = year,
              values_from = value) %>%
  rename('diff_2017' = '2017',
         'diff_2018' = '2018',
         'diff_2019' = '2019')

write.csv(x = left_join(cover_summary, effect_summary) %>%
  left_join(taxons %>% select(Label, Genus, Species, Group, Provenance), by = c('name' = 'Label')),
          file = "../Data/coverchange_summary.csv")

```

