---
title: "R Notebook"
output: html_notebook
---
# Random and spatial permutations:

## Loading packages and data:

# Initial data exploration:

Can use this part of the notebook just to check that things are working properly

```{r}
# Packages
library(tidyverse) #dplyr, tidyr, ggplot

# Random accumulation curves ###################################################

rpq0 <- read.csv("randompermutations_q0.csv", header = TRUE, stringsAsFactors = FALSE)
rpq0 <- rpq0 %>% gather(value = "div", key = "samp", -c(1:7))
rpq0$samp <- as.numeric(gsub("X", "", rpq0$samp))

rpq1 <- read.csv("randompermutations_q1.csv", header = TRUE, stringsAsFactors = FALSE)
rpq1 <- rpq1 %>% gather(value = "div", key = "samp", -c(1:7))
rpq1$samp <- as.numeric(gsub("X", "", rpq1$samp))

rpq2 <- read.csv("randompermutations_q2.csv", header = TRUE, stringsAsFactors = FALSE)
rpq2 <- rpq2 %>% gather(value = "div", key = "samp", -c(1:7))
rpq2$samp <- as.numeric(gsub("X", "", rpq2$samp))

# Spatial accumulation curves
spatcurves <- read.csv("spatial_accumulation.csv", header = TRUE, stringsAsFactors = FALSE)
spq0 <- spatcurves %>% filter(q == 0)
spq1 <- spatcurves %>% filter(q == 1)
spq2 <- spatcurves %>% filter(q == 2)

```


```{r}
sitename <- "HREC"
blockno <- 2
yearval <- 2018

rpq0 %>% filter(site == sitename & block == blockno & year == yearval) %>%
  ggplot(aes(x = samp,
             y = div,
             color = as.factor(fert),
             group = perm)) +
  geom_point(alpha = .01) + 
  geom_line(data = spq0 %>% filter(site == sitename & block == blockno & year == yearval),
            aes(x = samp,
                y = div,
                group = NULL,
                color = as.factor(fert)))
```

```{r}
rpq1 %>% filter(site == sitename & block == blockno & year == yearval) %>%
  ggplot(aes(x = samp,
             y = div,
             color = as.factor(fert),
             group = perm)) +
  geom_point(alpha = .01) + 
  geom_line(data = spq1 %>% filter(site == sitename & block == blockno & year == yearval),
            aes(x = samp,
                y = div,
                group = NULL,
                color = as.factor(fert)))
```

```{r}
rpq2 %>% filter(site == sitename & block == blockno & year == yearval) %>%
  ggplot(aes(x = samp,
             y = div,
             color = as.factor(fert),
             group = perm)) +
  geom_point(alpha = .01) + 
  geom_line(data = spq2 %>% filter(site == sitename & block == blockno & year == yearval),
            aes(x = samp,
                y = div,
                group = NULL,
                color = as.factor(fert)))
```

# Differences between random accumulation curves:

```{r}
# Random permutation summary ###################################################

# Q0
sumstatsq0 <- rpq0 %>% select(-X) %>% spread(key = fert, div)
colnames(sumstatsq0)[7:8] = c("uf_random", "f_random")
sumstatsq0$rand_diff <- -(sumstatsq0$uf_random - sumstatsq0$f_random)
sumstatsq0$rand_propdiff <- sumstatsq0$rand_diff / sumstatsq0$uf_random

# Q1
sumstatsq1 <- rpq1 %>% select(-X) %>% spread(key = fert, div)
colnames(sumstatsq1)[7:8] = c("uf_random", "f_random")
sumstatsq1$rand_diff <- -(sumstatsq1$uf_random - sumstatsq1$f_random)
sumstatsq1$rand_propdiff <- sumstatsq1$rand_diff / sumstatsq1$uf_random

# Q2
sumstatsq2 <- rpq2 %>% select(-X) %>% spread(key = fert, div)
colnames(sumstatsq2)[7:8] = c("uf_random", "f_random")
sumstatsq2$rand_diff <- -(sumstatsq2$uf_random - sumstatsq2$f_random)
sumstatsq2$rand_propdiff <- sumstatsq2$rand_diff / sumstatsq2$uf_random

# Spatial permutation summary ###################################################
statsq0 = spq0 %>% select(-X) %>% spread(key = fert, div)
colnames(statsq0)[7:8] = c("Unfert", "Fert")
statsq0$diff <- -(statsq0$Unfert - statsq0$Fert)
statsq0$propdiff <- statsq0$diff / statsq0$Unfert

statsq1 = spq1 %>% select(-X) %>% spread(key = fert, div)
colnames(statsq1)[7:8] = c("Unfert", "Fert")
statsq1$diff <- -(statsq1$Unfert - statsq1$Fert)
statsq1$propdiff <- statsq1$diff / statsq1$Unfert

statsq2 = spq2 %>% select(-X) %>% spread(key = fert, div)
colnames(statsq2)[7:8] = c("Unfert", "Fert")
statsq2$diff <- -(statsq2$Unfert - statsq2$Fert)
statsq2$propdiff <- statsq2$diff / statsq2$Unfert

head(sumstatsq0)
head(statsq0)
```

# Need to generate summary table with:

* Mean difference in random curves
* Confidence intervals (50, 95, 97.5, 99)
* Plots with mean difference in random accumulation curves relative to spatial
* Plots with mean difference between random accumulation curves relative to spatial

```{r}
conf_q0 <- sumstatsq0 %>% group_by(site, block, year, samp) %>%
  filter(site != "HREC") %>%
  summarise(mean_U = mean(uf_random),
            mean_F = mean(f_random),
            mean_diff = mean(rand_diff), 
            mean_prop = mean(rand_propdiff),
            percent_995 = quantile(rand_diff, .995),
            percent_975 = quantile(rand_diff, .975),
            percent_95 = quantile(rand_diff, .95),
            percent_005 = quantile(rand_diff, .005),
            percent_025 = quantile(rand_diff, .025),
            percent_05 = quantile(rand_diff, .05))

conf_q1 <- sumstatsq1 %>% group_by(site, block, year, samp) %>%
  filter(site != "HREC") %>%
  summarise(mean_U = mean(uf_random),
            mean_F = mean(f_random),
            mean_diff = mean(rand_diff), 
            mean_prop = mean(rand_propdiff),
            percent_995 = quantile(rand_diff, .995),
            percent_975 = quantile(rand_diff, .975),
            percent_95 = quantile(rand_diff, .95),
            percent_005 = quantile(rand_diff, .005),
            percent_025 = quantile(rand_diff, .025),
            percent_05 = quantile(rand_diff, .05))

conf_q2 <- sumstatsq2 %>% group_by(site, block, year, samp) %>%
  filter(site != "HREC") %>%
  summarise(mean_U = mean(uf_random),
            mean_F = mean(f_random ),
            mean_diff = mean(rand_diff), 
            mean_prop = mean(rand_propdiff),
            percent_995 = quantile(rand_diff, .995),
            percent_975 = quantile(rand_diff, .975),
            percent_95 = quantile(rand_diff, .95),
            percent_005 = quantile(rand_diff, .005),
            percent_025 = quantile(rand_diff, .025),
            percent_05 = quantile(rand_diff, .05))
```

# Plotting lines to show confidence intervals

```{r}
sitename <- "SFREC"
blockno <- 4
yearval <- 2017

conf_q2 %>% filter(site == sitename & block == blockno & year == yearval) %>%
  ggplot(aes(x = samp)) +
  geom_line(aes(y = mean_diff)) +
  geom_line(aes(y = percent_975), lty = 2) +
  geom_line(aes(y = percent_025), lty = 2) +
  geom_line(aes(y = percent_995), lty = 3) +
  geom_line(aes(y = percent_005), lty = 3) +
  geom_line(aes(y = percent_95), lty = 4) +
  geom_line(aes(y = percent_05), lty = 4) +
  geom_line(data = statsq2 %>% filter(site == sitename & block == blockno & year == yearval),
            aes(x = samp,
                y = diff),
            color = "red")
```

# Steps to calculate confidence intervals for the whole site

* Calculate means and join datasets together

    * Unclear what the best way is to calculate sitewide differences in means - improper to take the average of different confidence intervals, rather than the mean of each permutation

* Plot mean total effect change

* Plot mean random effect change

* Plot net effect change

  * Add confidence intervals

```{r}
site_conf_q0 <- sumstatsq0 %>% 
  filter(!(site == "HREC")) %>%
  group_by(year, samp, perm) %>%
  summarise(meandiff = mean(rand_diff)) %>%
  group_by(year, samp) %>%
  summarise(mean_diff = mean(meandiff), 
            percent_995 = quantile(meandiff, .995),
            percent_975 = quantile(meandiff, .975),
            percent_95 = quantile(meandiff, .95),
            percent_005 = quantile(meandiff, .005),
            percent_025 = quantile(meandiff, .025),
            percent_05 = quantile(meandiff, .05))

site_conf_q1 <- sumstatsq1 %>% 
  filter(!(site == "HREC")) %>%
  group_by(year, samp, perm) %>%
  summarise(meandiff = mean(rand_diff)) %>%
  group_by(year, samp) %>%
  summarise(mean_diff = mean(meandiff), 
            percent_995 = quantile(meandiff, .995),
            percent_975 = quantile(meandiff, .975),
            percent_95 = quantile(meandiff, .95),
            percent_005 = quantile(meandiff, .005),
            percent_025 = quantile(meandiff, .025),
            percent_05 = quantile(meandiff, .05))

site_conf_q2 <- sumstatsq2 %>% 
  filter(!(site == "HREC")) %>%
  group_by(year, samp, perm) %>%
  summarise(meandiff = mean(rand_diff)) %>%
  group_by(year, samp) %>%
  summarise(mean_diff = mean(meandiff), 
            percent_995 = quantile(meandiff, .995),
            percent_975 = quantile(meandiff, .975),
            percent_95 = quantile(meandiff, .95),
            percent_005 = quantile(meandiff, .005),
            percent_025 = quantile(meandiff, .025),
            percent_05 = quantile(meandiff, .05))
```

# Q = 0 

```{r}
# Site to filter:
 # MCLA 1
 # HREC 1
to_join <- statsq0 %>%  filter(!(site == "HREC"))

test <- inner_join(to_join, site_conf_q0)

test %>% 
  group_by(year, samp) %>%
  summarise_if(is.numeric, mean) %>%
  ggplot(aes(x = samp)) +
  geom_line(aes(y= diff), color = "red") + 
  geom_line(aes(y = percent_975), lty = 2) +
  geom_line(aes(y = percent_025), lty = 2) +
  geom_line(aes(y = percent_995), lty = 3) +
  geom_line(aes(y = percent_005), lty = 3) +
  geom_line(aes(y = percent_95), lty = 4) +
  geom_line(aes(y = percent_05), lty = 4) +
  facet_wrap(~year) +
  geom_hline(yintercept = 0)
```
```{r}
# Site to filter:
 # MCLA 1
 # HREC 1

to_join <- statsq1 %>% filter(!(site == "HREC"))

test <- inner_join(to_join, site_conf_q1)

test %>% 
  group_by(year, samp) %>%
  summarise_if(is.numeric, mean) %>%
  ggplot(aes(x = samp)) +
  geom_line(aes(y= diff), color = "red") + 
  geom_line(aes(y= mean_diff)) +
  geom_line(aes(y = percent_975), lty = 2) +
  geom_line(aes(y = percent_025), lty = 2) +
  geom_line(aes(y = percent_995), lty = 3) +
  geom_line(aes(y = percent_005), lty = 3) +
  geom_line(aes(y = percent_95), lty = 4) +
  geom_line(aes(y = percent_05), lty = 4) +
  facet_wrap(~year) +
  geom_hline(yintercept = 0)

```

```{r}
# Site to filter:
 # MCLA 1
 # HREC 1

to_join <- statsq0 %>% filter(!(site == "HREC"))

test <- inner_join(to_join, site_conf_q0)

test %>% 
  filter(year == 2018) %>%
  group_by(year, samp) %>%
  summarise_if(is.numeric, mean) %>%
  ggplot(aes(x = samp)) +
  # geom_ribbon(aes(ymin = percent_005 / Unfert, ymax = percent_995 / Unfert), 
  #             alpha = .4, fill = "lightblue", color = "black", lty = 2) +
  # geom_ribbon(aes(ymin = percent_025 / Unfert, ymax = percent_975 / Unfert), 
  #             alpha = .4, fill = "lightblue", color = "black", lty = 2) +
  # geom_ribbon(aes(ymin = percent_05 / Unfert, ymax = percent_95 / Unfert), 
  #             alpha = .4, fill = "lightblue", color = "black", lty = 2) +
  # geom_line(aes(y= mean_diff / Unfert), size = 2) +
  geom_line(aes(y= diff / Unfert), color = "black", size = 2) + 
  geom_hline(yintercept = 0) +
  ylim(-.15, 0) +
  ylab("Proportion Diversity Change") + 
  xlab("Sampling Effort") +
  theme(text = element_text(size = 15, face = "bold")) +
  theme(panel.background = element_rect(fill = "white"),
        plot.background = element_rect(fill = "white")) + 
  theme(panel.grid.major = element_line(colour = "grey85"))

ggsave(filename = "Figures/netchange_q0_spatial.jpeg", height = 5, width = 5)

test %>% 
  filter(year == 2018) %>%
  group_by(year, samp) %>%
  summarise_if(is.numeric, mean) %>%
  ggplot(aes(x = samp)) +
  # geom_ribbon(aes(ymin = percent_005 / Unfert, ymax = percent_995 / Unfert), 
  #             alpha = .4, fill = "lightblue", color = "black", lty = 2) +
  geom_ribbon(aes(ymin = mean_diff / Unfert, ymax =diff / Unfert), 
               alpha = .5, fill = "forestgreen", color = "black", lty = 2, alpha = .5) +
  geom_line(aes(y = percent_025 / Unfert),  color = "black", lty = 2, size = 1) +
  geom_line(aes(y = percent_975 / Unfert),  color = "black", lty = 2, size = 1) +
  # geom_ribbon(aes(ymin = percent_05 / Unfert, ymax = percent_95 / Unfert), 
  #             alpha = .4, fill = "lightblue", color = "black", lty = 2) +
  geom_line(aes(y= mean_diff / Unfert), size = 2, lty = 2) +
  geom_line(aes(y= diff / Unfert), color = "black", size = 2) + 
  geom_hline(yintercept = 0) +
  ylim(-.15, 0) +
  ylab("Proportion Diversity Change") + 
  xlab("Sampling Effort") +
  theme(text = element_text(size = 15, face = "bold")) +
  theme(panel.background = element_rect(fill = "white"),
        plot.background = element_rect(fill = "white")) + 
  theme(panel.grid.major = element_line(colour = "grey85"))

ggsave(filename = "Figures/netchange_q0_random.jpeg", height = 5, width = 5)

```

```{r}
to_join <- statsq0 %>% filter(!(site == "HREC")) 

test <- inner_join(to_join, site_conf_q0)

test %>% 
  filter(year == 2018) %>%
  group_by(year, samp) %>%
  summarise_if(is.numeric, mean) %>%
  filter(year == 2018) %>%
  ggplot(aes(x = samp)) +
  annotate("text", x = 32, y = .035, label = "Agg. Effect Greater in Control", alpha = .4, size = 6) + 
  annotate("text", x = 32, y = -.035, label = "Agg. Effect Greater in Treatment", alpha = .4, size = 6) +
  # geom_ribbon(aes(ymin = percent_005 / Unfert - mean_diff / Unfert, 
  #                 ymax = percent_995 / Unfert - mean_diff / Unfert), 
  #             alpha = .4, fill = "lightblue", color = "black", lty = 2) +
  geom_ribbon(aes(ymin = percent_025 / Unfert - mean_diff / Unfert, 
                  ymax = percent_975 / Unfert  - mean_diff / Unfert), 
              alpha = .4, fill = "white", color = "black", lty = 2) +
    # geom_ribbon(aes(ymin = percent_05 / Unfert - mean_diff / Unfert, 
    #               ymax = percent_95 / Unfert  - mean_diff / Unfert), 
    #           alpha = .4, fill = "lightblue", color = "black", lty = 2) +
  geom_line(aes(y= mean_diff / Unfert - mean_diff / Unfert), size = 1, lty = 2) +
  geom_line(aes(y= diff / Unfert  - mean_diff / Unfert), color = "forestgreen", size = 2) + 
  ylab("Net Aggregation Effect") + 
  xlab("Sampling Effort") +
  ylim(-.04, .04) +
  theme(text = element_text(size = 15, face = "bold")) +
  theme(panel.background = element_rect(fill = "white"),
        plot.background = element_rect(fill = "white"))  + 
  theme(panel.grid.major = element_line(colour = "grey85"))

ggsave(filename = "Figures/aggeffect_q0.jpeg", height = 5, width = 5)

```

```{r}
# Site to filter:
 # MCLA 1
 # HREC 1

to_join <- statsq2 %>% filter(!(site == "HREC"))

test <- inner_join(to_join, site_conf_q2)

test %>% 
  filter(year == 2018) %>%
  group_by(year, samp) %>%
  summarise_if(is.numeric, mean) %>%
  ggplot(aes(x = samp)) +
  # geom_ribbon(aes(ymin = percent_005 / Unfert, ymax = percent_995 / Unfert), 
  #             alpha = .4, fill = "lightblue", color = "black", lty = 2) +
  # geom_ribbon(aes(ymin = percent_025 / Unfert, ymax = percent_975 / Unfert), 
  #             alpha = .4, fill = "lightblue", color = "black", lty = 2) +
  # geom_ribbon(aes(ymin = percent_05 / Unfert, ymax = percent_95 / Unfert), 
  #             alpha = .4, fill = "lightblue", color = "black", lty = 2) +
  # geom_line(aes(y= mean_diff / Unfert), size = 2) +
  geom_line(aes(y= diff / Unfert), color = "black", size = 2) + 
  geom_hline(yintercept = 0) +
  ylim(-.20, 0) +
  ylab("Proportion Diversity Change") + 
  xlab("Sampling Effort") +
  theme(text = element_text(size = 15, face = "bold")) +
  theme(panel.background = element_rect(fill = "white"),
        plot.background = element_rect(fill = "white")) + 
  theme(panel.grid.major = element_line(colour = "grey85"))

ggsave(filename = "Figures/netchange_q2_spatial.jpeg", height = 5, width = 5)

test %>% 
  filter(year == 2018) %>%
  group_by(year, samp) %>%
  summarise_if(is.numeric, mean) %>%
  ggplot(aes(x = samp)) +
  # geom_ribbon(aes(ymin = percent_005 / Unfert, ymax = percent_995 / Unfert), 
  #             alpha = .4, fill = "lightblue", color = "black", lty = 2) +
  geom_ribbon(aes(ymin = mean_diff / Unfert, ymax =diff / Unfert), 
               alpha = .5, fill = "forestgreen", color = "black", lty = 2, alpha = .5) +
  geom_line(aes(y = percent_025 / Unfert),  color = "black", lty = 2, size = 1) +
  geom_line(aes(y = percent_975 / Unfert),  color = "black", lty = 2, size = 1) +
  # geom_ribbon(aes(ymin = percent_05 / Unfert, ymax = percent_95 / Unfert), 
  #             alpha = .4, fill = "lightblue", color = "black", lty = 2) +
  geom_line(aes(y= mean_diff / Unfert), size = 2, lty = 2) +
  geom_line(aes(y= diff / Unfert), color = "black", size = 2) + 
  geom_hline(yintercept = 0) +
  ylim(-.2, 0) +
  ylab("Proportion Diversity Change") + 
  xlab("Sampling Effort") +
  theme(text = element_text(size = 15, face = "bold")) +
  theme(panel.background = element_rect(fill = "white"),
        plot.background = element_rect(fill = "white")) + 
  theme(panel.grid.major = element_line(colour = "grey85"))

ggsave(filename = "Figures/netchange_q2_random.jpeg", height = 5, width = 5)
```


```{r}
to_join <- statsq2 %>% filter(!(site == "HREC")) 

test <- inner_join(to_join, site_conf_q2)

test %>% 
  filter(year == 2018) %>%
  group_by(year, samp) %>%
  summarise_if(is.numeric, mean) %>%
  filter(year == 2018) %>%
  ggplot(aes(x = samp)) +
  annotate("text", x = 32, y = .035, label = "Agg. Effect Greater in Control", alpha = .4, size = 6) + 
  annotate("text", x = 32, y = -.035, label = "Agg. Effect Greater in Treatment", alpha = .4, size = 6) +
  # geom_ribbon(aes(ymin = percent_005 / Unfert - mean_diff / Unfert, 
  #                 ymax = percent_995 / Unfert - mean_diff / Unfert), 
  #             alpha = .4, fill = "lightblue", color = "black", lty = 2) +
  geom_ribbon(aes(ymin = percent_025 / Unfert - mean_diff / Unfert, 
                  ymax = percent_975 / Unfert  - mean_diff / Unfert), 
              alpha = .4, fill = "white", color = "black", lty = 2) +
    # geom_ribbon(aes(ymin = percent_05 / Unfert - mean_diff / Unfert, 
    #               ymax = percent_95 / Unfert  - mean_diff / Unfert), 
    #           alpha = .4, fill = "lightblue", color = "black", lty = 2) +
  geom_line(aes(y= mean_diff / Unfert - mean_diff / Unfert), size = 1, lty = 2) +
  geom_line(aes(y= diff / Unfert  - mean_diff / Unfert), color = "forestgreen", size = 2) + 
  ylab("Net Aggregation Effect") + 
  xlab("Sampling Effort") +
  ylim(-.04, .04) +
  theme(text = element_text(size = 15, face = "bold")) +
  theme(panel.background = element_rect(fill = "white"),
        plot.background = element_rect(fill = "white"))  + 
  theme(panel.grid.major = element_line(colour = "grey85"))

ggsave(filename = "Figures/aggeffect_q2.jpeg", height = 5, width = 5)

```

### OLD VERSION ################################################################
# Q = 0 

```{r}
# Site to filter:
 # MCLA 1
 # HREC 1
to_join <- statsq0 %>% filter(!(site == "HREC")) 
  
test <- inner_join(to_join, site_conf_q0)

test %>% 
  group_by(year, samp) %>%
  summarise_if(is.numeric, mean) %>%
  filter(year == 2018) %>%
  ggplot(aes(x = samp)) +
  geom_line(aes(y= mean_diff - diff), color = "red") +
  geom_line(aes(y = percent_975- mean_diff), lty = 2) +
  geom_line(aes(y = percent_025- mean_diff), lty = 2) +
  geom_line(aes(y = percent_995- mean_diff), lty = 3) +
  geom_line(aes(y = percent_005- mean_diff), lty = 3) +
  geom_line(aes(y = percent_95- mean_diff), lty = 4) +
  geom_line(aes(y = percent_05- mean_diff), lty = 4) +
  facet_wrap(~year) +
  geom_hline(yintercept = 0) +
  ylab("Mean Aggregation Effect") + 
  xlab("Sample Number") +
  ggtitle("Aggregation Effect (Richness)")

ggsave(filename = "Presentation Figures/aggeffectq0.jpeg")
```

```{r}
# Site to filter:
 # MCLA 1
 # HREC 1

to_join <- statsq1 %>% filter(!(site == "HREC"))

test <- inner_join(to_join, site_conf_q1)

test %>% 
  group_by(year, samp) %>%
  summarise_if(is.numeric, mean) %>%
  ggplot(aes(x = samp)) +
  geom_line(aes(y= diff - mean_diff), color = "red") + 
  geom_line(aes(y = percent_975 - mean_diff), lty = 2) +
  geom_line(aes(y = percent_025 - mean_diff), lty = 2) +
  geom_line(aes(y = percent_995 - mean_diff), lty = 3) +
  geom_line(aes(y = percent_005 - mean_diff), lty = 3) +
  geom_line(aes(y = percent_95- mean_diff), lty = 4) +
  geom_line(aes(y = percent_05- mean_diff), lty = 4) +
  facet_wrap(~year) +
  geom_hline(yintercept = 0)

```

```{r}
# Site to filter:
 # MCLA 1
 # HREC 1

to_join <- statsq2 %>% filter(!(site == "HREC"))
  
test <- inner_join(to_join, site_conf_q2)

test %>%
  group_by(year, samp) %>%
  summarise_if(is.numeric, mean) %>%
  filter(year == 2018) %>%
  ggplot(aes(x = samp)) +
  geom_line(aes(y= mean_diff - diff), color = "red") + 
  geom_line(aes(y = mean_diff - diff, group = paste(site, block)), alpha = .1, data = test %>% filter(year == 2018)) +
  geom_line(aes(y = percent_975- mean_diff), lty = 2) +
  geom_line(aes(y = percent_025- mean_diff), lty = 2) +
  geom_line(aes(y = percent_995- mean_diff), lty = 3) +
  geom_line(aes(y = percent_005- mean_diff), lty = 3) +
  geom_line(aes(y = percent_95- mean_diff), lty = 4) +
  geom_line(aes(y = percent_05- mean_diff), lty = 4) +
  facet_wrap(~year) +
  geom_hline(yintercept = 0) +
  ylab("Mean Aggregation Effect") + 
  xlab("Sample Number") +
  ggtitle("Aggregation Effect (InvSimpson)")


View(test)
ggsave("Presentation Figures/aggeffectq2.jpeg")

```

