---
title: "Two-scale analysis with permutations"
output: html_notebook
---

```{r}
library(lmPerm)
library(dplyr)
source("ens_specaccum.R")

final_merged <- read.csv("../final_2018.csv", header = TRUE, stringsAsFactors = FALSE)
head(final_merged)[,1:20]
```

```{r}
com.mat <- final_merged %>% select(- one_of("site", "block", "plot", "subplot", "x", "y", 
                                            "note", "index", "year", "sitename", "dateestablished", 
                                            "plotlocation", "fertilized", "X"))
com.attr <-  final_merged %>% select(one_of("site", "block", "plot", "subplot", "x", "y", 
                                            "note", "index", "year", "sitename", "dateestablished", 
                                            "plotlocation", "fertilized"))

dfun = d_calc

com_norm <- normalize_rows(com.mat)
unique(rowSums(com_norm)) == 1

# Sample (alpha) diversity
alpha_q0 = apply(com_norm, 1, dfun, q = 0, sample.weight = 1)
alpha_q1 = apply(com_norm, 1, dfun, q = 1, sample.weight = 1)
alpha_q2 = apply(com_norm, 1, dfun, q = 2, sample.weight = 1)

# Combining alpha statistics to a single dataframe
alpha.stats <- cbind(com.attr, alpha_q0, alpha_q1, alpha_q2) %>% 
  group_by(site, block, plot, fertilized, year) %>%
  summarise_at(c("alpha_q0", "alpha_q1", "alpha_q2"), mean)

alpha.raw <- cbind(com.attr, alpha_q0, alpha_q1, alpha_q2)

# Aggregating to generate gamma diversity matrix
com.gamma <- bind_cols(select(com.attr, site, block, plot, year, fertilized), com.mat) %>% 
  group_by(site, block, plot, year, fertilized) %>%
  summarise_all(sum)

# Generating gamma diversity dataset
gamma.attr <- com.gamma[,1:5]
gamma.norm <- normalize_rows(com.gamma[,-(1:5)])

# Total (gamma) diversity
gamma_q0 = apply(gamma.norm, 1, dfun, q = 0, sample.weight = 1)
gamma_q1 = apply(gamma.norm, 1, dfun, q = 1, sample.weight = 1)
gamma_q2 = apply(gamma.norm, 1, dfun, q = 2, sample.weight = 1)

gamma.stats <- cbind(data.frame(gamma.attr), gamma_q0, gamma_q1, gamma_q2)

# Combining into a single dataframe
alldiv.stats <- inner_join(alpha.stats, gamma.stats) %>%
  mutate(beta_q0 = gamma_q0 / alpha_q0,
         beta_q1 = gamma_q1 / alpha_q1,
         beta_q2 = gamma_q2 / alpha_q2)
```

# Statistical analysis:

## What is the correct model structure:

* Repeated measures (each plot over time)
* Blocking and within-site variance
* Treatment effects (1 and 2 years)
* Treatment treated as linear vs. nonlinear?
* Interannual variation

## I think the most appropriate command is:

* Div ~ treatment x as.factor(year) + (1 | site/block)

# Alpha-scale analysis
```{r}
library(lme4)
library(lmerTest)

# Filter out one block at HREC?
alpha.raw <- alpha.raw %>% filter(! ((site == "HREC") & (block == 1))) 
head(alpha.raw)

alpha.raw$site <- as.factor(alpha.raw$site) # Site as factor
alpha.raw$block <- as.factor(alpha.raw$block) # Block as factor
alpha.raw$fert_num <- alpha.raw$fertilized * (alpha.raw$year - 2016)
alpha.raw$fertilized <- as.factor(alpha.raw$fertilized) # Fertilization as factor
alpha.raw$year <- alpha.raw$year - 2016 # Year as range of 1-2
alpha.raw$year <- as.factor(alpha.raw$year) # Y

```

```{r}
mod1_q0 <- lmer(alpha_q0 ~ factor(fert_num) + factor(year) + (1|site) + (1|site:block), data = alpha.raw)
summary(mod1_q0)
anova(mod1_q0)
qqnorm(scale(resid(mod1_q0)))
abline(b = 1, a = 0)
```

```{r}
mod1_q1 <- lmer(alpha_q1 ~ factor(fert_num) + factor(year) + (1|site) + (1|site:block), data = alpha.raw)
summary(mod1_q1)
anova(mod1_q1)
qqnorm(scale(resid(mod1_q1)))
abline(b = 1, a = 0)
```
```{r}
mod1_q2 <- lmer(alpha_q2 ~ factor(fert_num) + factor(year) + (1|site) + (1|site:block), data = alpha.raw)
summary(mod1_q2)
anova(mod1_q2)
qqnorm(scale(resid(mod1_q2)))
abline(b = 1, a = 0)
```

# Gamma and beta diversity analysis

- Question of whether or not to normalize prior to analysis?

```{r}

# For a given matrix
permtest <- function(com.mat, qval, perm){
  
  require(testthat)
  
  # Take all the rows and split them into two groups
  alpha.split <- base::sample(x = c(1:nrow(com.mat)), size = (nrow(com.mat) / 2))
  com.F <- com.mat[alpha.split,]
  com.UF <- com.mat[-(alpha.split),]
  
  # Equal sizes?
  expect_true(nrow(com.F) == nrow(com.UF))
  
  # Normalize, calc alpha diversity of each group and store
  alpha_fert <- apply(normalize_rows(com.F), 1, dfun, q = qval, sample.weight = 1)
  alpha_unfert <- apply(normalize_rows(com.UF), 1, dfun, q = qval, sample.weight = 1)
  
  # Aggregate up to the gamma scale
  gam.F <-apply(com.F, 2, sum)
  gam.UF <- apply(com.UF, 2, sum)
  
  # Calculate gamma level diversity statistics
  gamma_fert = dfun(gam.F/ sum(gam.F), q = qval, sample.weight = 1)
  gamma_unfert = dfun(gam.UF/ sum(gam.UF), q = qval, sample.weight = 1)

  # Calculate beta diversity of each group and store
  beta_fert = gamma_fert / mean(alpha_fert)
  beta_unfert = gamma_unfert / mean(alpha_unfert)

  # Return data set
  return(data.frame(fert = c(1, 0),
                    perm = c(perm, perm),
                    alpha = c(mean(alpha_fert), mean(alpha_unfert)),
                    beta = c(beta_fert, beta_unfert),
                    gamma = c(gamma_fert, gamma_unfert)))
  
}

permtest(com.mat, qval = 0, perm = 1)

```

# Repeat for each value of Q

# Q = 0
```{r}

permtest_repeat <- function(com.mat, qval, perm, perm.total){
  
  output <- list()
  while(perm < perm.total){
    permstore <- permtest(com.mat, qval, perm)
    output[[perm]] <- data.frame(permstore)
    perm <- perm + 1
  }
  return(bind_rows(output))
}

full_perm <- com.attr %>% select(site, block, year) %>%
  bind_cols(com.mat) %>%
  group_by(site, block, year) %>%
  do(permtest_repeat(.[4:ncol(.)], qval = 0, perm = 1, perm.total = 99999))

write.csv(x = full_perm, "../twoscale_perm_q0.csv")
```

```{r}
library(ggplot2)
perm_summary <- full_perm %>% group_by(site, block, year, perm) %>%
  summarise(diff_alpha = alpha[fert == 0] - alpha[fert == 1],
            diff_beta = beta[fert == 0] - beta[fert == 1],
            diff_gamma = gamma[fert == 0] - gamma[fert == 1])

perm_summary %>% 
  ggplot(aes(x = diff_alpha, color = as.factor(year))) +
  geom_density() +
  facet_grid(block~site)
```
```{r}
perm_summary %>% 
  ggplot(aes(x = diff_beta, color = as.factor(year))) +
  geom_density() +
  facet_grid(block~site)
```

```{r}
perm_summary %>% 
  ggplot(aes(x = diff_gamma, color = as.factor(year))) +
  geom_density() +
  facet_grid(block~site)
```


# Q = 1
```{r}
perm.total <- 10

permtest_repeat <- function(com.mat, qval, perm, perm.total){
  
  output <- list()
  while(perm < perm.total){
    permstore <- permtest(com.mat, qval, perm)
    output[[perm]] <- data.frame(permstore)
    perm <- perm + 1
  }
  return(bind_rows(output))
}

full_perm <- com.attr %>% select(site, block, year) %>%
  bind_cols(com.mat) %>%
  group_by(site, block, year) %>%
  do(permtest_repeat(.[4:ncol(.)], qval = 1, perm = 1, perm.total = 9999))

write.csv(x = full_perm, "../twoscale_perm_q1.csv")

```

```{r}
library(ggplot2)
perm_summary <- full_perm %>% group_by(site, block, year, perm) %>%
  summarise(diff_alpha = alpha[fert == 0] - alpha[fert == 1],
            diff_beta = beta[fert == 0] - beta[fert == 1],
            diff_gamma = gamma[fert == 0] - gamma[fert == 1])

perm_summary %>% 
  ggplot(aes(x = diff_alpha, color = as.factor(year))) +
  geom_density() +
  facet_grid(block~site)
```
```{r}
perm_summary %>% 
  ggplot(aes(x = diff_beta, color = as.factor(year))) +
  geom_density() +
  facet_grid(block~site)
```

```{r}
perm_summary %>% 
  ggplot(aes(x = diff_gamma, color = as.factor(year))) +
  geom_density() +
  facet_grid(block~site)
```


# Q = 2
```{r}
perm.total <- 10

permtest_repeat <- function(com.mat, qval, perm, perm.total){
  
  output <- list()
  while(perm < perm.total){
    permstore <- permtest(com.mat, qval, perm)
    output[[perm]] <- data.frame(permstore)
    perm <- perm + 1
  }
  return(bind_rows(output))
}

full_perm <- com.attr %>% select(site, block, year) %>%
  bind_cols(com.mat) %>%
  group_by(site, block, year) %>%
  do(permtest_repeat(.[4:ncol(.)], qval = 2, perm = 1, perm.total = 9999))

write.csv(x = full_perm, "../twoscale_perm_q2.csv")
```

```{r}
library(ggplot2)
perm_summary <- full_perm %>% group_by(site, block, year, perm) %>%
  summarise(diff_alpha = alpha[fert == 0] - alpha[fert == 1],
            diff_beta = beta[fert == 0] - beta[fert == 1],
            diff_gamma = gamma[fert == 0] - gamma[fert == 1])

perm_summary %>% 
  ggplot(aes(x = diff_alpha, color = as.factor(year))) +
  geom_density() +
  facet_grid(block~site)
```
```{r}
perm_summary %>% 
  ggplot(aes(x = diff_beta, color = as.factor(year))) +
  geom_density() +
  facet_grid(block~site)
```

```{r}
perm_summary %>% 
  ggplot(aes(x = diff_gamma, color = as.factor(year))) +
  geom_density() +
  facet_grid(block~site)
```

